% Created 2020-12-05 Sat 19:29
% Intended LaTeX compiler: xelatex
\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Feng Xia}
\date{\today}
\title{Feng's Emacs configuration}
\hypersetup{
 pdfauthor={Feng Xia},
 pdftitle={Feng's Emacs configuration},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.4)},
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

I have seen others using org-mode to mangae emacs config, and they
came out very nicely. Finally, after 4 years of using emacs, I ran
into \href{https://github.com/pascalfleury/emacs-config}{Pascal Fleury} portal emacs config, and it makes sense to me!!
After trying it out for a couple weeks now, I really like it! So now
after the configs are stable to my taste, and is also growing slowly
when I add new packages and custom stuff, I find the original sections
a bit, confusing. So I'm to take his copy and rearrange it so it fits
my way of thinking. I will not change the fundamental things such as
\texttt{tangle}, but will clarify what the packages and configs are about.

\section{the idea}
\label{sec:org28571e1}

This idea is actually a bit chicken-egg: in order to tangle, you must
first fire up emacs, then convert this org to \texttt{.el}, then load it back
into emacs to take effect.

The key here are relying on two things:

\begin{enumerate}
\item There are two version of the \texttt{emacs\_setup.el} file, one is a dummy
short version that gets loaded for the very first time. This is the
same stuff you can recreate using the \ref{sec:org4bb977e}: \texttt{C-c C-v t}.
\item In the default \texttt{.emacs, write one line: to load this =.el} file. Then,
it short version will tangle this org file, and write over itself
(on disk), thus literally replaced itself w/ more contents. At this
point, it will tangle all the code blocks in this file, and at the
end of it, it will call to \hyperref[sec:org7bb9a16]{recompile packages}, thus kicking off the
entire download, compiling, installation and configuration.
\end{enumerate}

\section{deps}
\label{sec:orgfbdce36}

There are some host packages/tools you need to install. These are not
hard dependencies, but really, it works better that way if they are there.

I have been thinking how to handle them. The original author uses
tangle to create a bash file. So the idea is to run this \texttt{.sh}
first. But then, I think there are two problems:

\begin{enumerate}
\item host package manager is different, eg. \texttt{apt} for Ubuntu, and \texttt{yum} for Cent.
\item package name changes sometimes, and not mention, the packages are
completely different among distributions.

So all in all, I think it's much better to simply list what I want
to have, and then let some offline research/google to handle how to
install them. Another idea is to build a Docker image w/ all thest
inside. Hmm\ldots{} I may try that someday.
\end{enumerate}

\subsection{what I want to use}
\label{sec:org3bf0e73}

I'll simply keep a list:

\begin{enumerate}
\item \href{https://github.com/ggreer/the\_silver\_searcher}{silver searcher, aka. ag}
\item \href{https://github.com/nvm-sh/nvm}{nvm}: needed for Node
\item \href{https://prettier.io/docs/en/install.html}{prettier}: require Node first
\item sqlite3: needed by org-roam
\item \href{https://github.com/hakimel/reveal.js/}{reveal.js}: needed to enable org-export to reveal slides
\item \href{https://plantuml.com/download}{plantuml.jar}
\item \href{https://packages.ubuntu.com/search?keywords=mu4e}{mu4e} \& \href{https://packages.ubuntu.com/search?keywords=isync}{isync} (this give you \texttt{mbsync})
\item \href{https://github.com/mguessan/davmail}{davmail}
\end{enumerate}

\section{clean start}
\label{sec:orgd2eac0b}

\textbf{ASSUMPTION}:

\begin{enumerate}
\item you have installed emacs. Using v26.3 as of writing.
\item determine where to put this org file. Throughout this doc, we are
assuming \texttt{\textasciitilde{}/Emacs/} as the folder.
\end{enumerate}

Once you are here, starting from a clean sheet is pretty easy:

\begin{enumerate}
\item delete all your old \texttt{.emacs}, \texttt{.emacs.d}, or back them up somewhere.
\item tangle this org file into a \texttt{.el} file. To make things easier, I'm
going to include the \texttt{.el} in the repo. So just copy it.
\item create a \texttt{.emacs} file, and write one line \texttt{(load-file
   "\textasciitilde{}/Emacs/emacs\_setup.el")}, essentially tells emacs where to find
the initial config file.
\item make sure Emacs re-interprets its init (you could restart it).
\end{enumerate}

That's it. Just sit back and watch emacs download and compile things,
and after it's done, you will be given the power of this beautiful
editor, all configured and ready to go! Now to think of it, isn't this
what LOC is trying to achieve!?

\subsection{.emacs}
\label{sec:orga1aa6d1}

I have my config in directory \texttt{\textasciitilde{}/Emacs} which is where I clone this
repository. The config setup is maintained purely in the
\texttt{\textasciitilde{}/Emacs/emacs\_setup.org} file.

In your \texttt{\textasciitilde{}/.emacs} file, all you need to add is

\begin{verbatim}
;; Loads Feng's emacs setup with bootstrap
(load-file "~/Emacs/emacs_setup.el")
\end{verbatim}

\subsection{bootstrap .el}
\label{sec:org274852e}

Put this in the \texttt{\textasciitilde{}/Emacs/emacs\_setup.el}, and viola, it will regnerate itself!

\begin{verbatim}

;; This is the initial state of the file to be loaded.
;; It will replace itself with the actual configuration at first run.

(require 'org) ; We can't tangle without org!

(setq config_base (expand-file-name "emacs_setup"
            (file-name-directory
             (or load-file-name buffer-file-name))))
(find-file (concat config_base ".org"))        ; Open the configuration
(org-babel-tangle)                             ; tangle it
(load-file (concat config_base ".el"))         ; load it
(byte-compile-file (concat config_base ".el")) ; finally byte-compile it
\end{verbatim}
\section{reset}
\label{sec:orgf3fd964}

Reset takes two steps, but you can do either or both, depending on
what you are trying to reset.

\subsection{reset config}
\label{sec:orgb8322df}

If you have made a change to this org and what's to test drive it, you
need to either \ref{sec:org4bb977e} or just save this file to trigger \ref{sec:org242c211}. Sometimes, I found I have to go the \ref{sec:org4bb977e} route
because the hook is not fired. This is understandable that when I'm
changing this file, it may render a broken config, thus the hook and
all others can be in a comprised state when you start emacs.

\subsection{recompile all packages}
\label{sec:org7bb9a16}
This is the \textbf{RESET} button. This will force-recompile everything in
\texttt{\textasciitilde{}/.emacs.d/elpa/...} Just run \texttt{M-:} and then enter this:

\begin{verbatim}
(byte-recompile-directory package-user-dir nil 'force)
\end{verbatim}

or simply \texttt{C-x C-e} at the end of that line.

\textbf{Note} that by setting \texttt{:tangle no}, this piece of code will be included
into the \texttt{.el} file. So it stays inside this org. Nice.

\section{initialize emacs}
\label{sec:org88e1d04}

\subsection{info header}
\label{sec:org7070636}

Just to add a little information in the tangled file so you don't
\textbf{manually} mess with the generated \texttt{.el} file.

\begin{verbatim}
;; ===== this file was auto-tangled, only edit the emacs_setup.org =====
\end{verbatim}

\subsection{melpa}
\label{sec:orgf961fcc}

Make sure we have the package system initialized before we load anything.

\begin{verbatim}
(require 'package)
(when (< emacs-major-version 27)
  (package-initialize))
\end{verbatim}

Adding my choice of packages repositories.

\#+NAME melpa-setup
\begin{verbatim}
(setq package-archives '(("org" . "https://orgmode.org/elpa/")
                         ("stable-melpa" . "https://stable.melpa.org/packages/")
                         ("melpa" . "https://melpa.org/packages/")
                         ("gnu" . "https://elpa.gnu.org/packages/")
                         ; ("marmalade" . "https://marmalade-repo.org/packages/")
                        ))
\end{verbatim}

\subsection{use-package}
\label{sec:orgfc8a1eb}

I use \texttt{use-package} for most configuration, and that needs to be at the
top of the file.  \texttt{use-package} verifies the presence of the requested
package, otherwise installs it, and presents convenient sections for
configs of variables, key bindings etc. that happen only if the
package is actually loaded.

First, make sure it gets installed if it is not there yet.

\begin{verbatim}
;; make sure use-package is installed
(unless (package-installed-p 'use-package)
  (package-refresh-contents)
  (package-install 'use-package))
(require 'use-package)
\end{verbatim}

\begin{verbatim}
(eval-when-compile (require 'use-package))
\end{verbatim}

\subsection{tangle this config}
\label{sec:org7ffb906}
\subsubsection{manual tangle}
\label{sec:org4bb977e}

I have setup auto tangle in the header as \texttt{:tangle yes}. So upon save,
this org file will be tangled into an \texttt{.el} file, and that is the file
emacs should load.

Alternatively, use the \texttt{C-c C-v t} [org-babel-tangle] to do this
manually.

\subsubsection{auto tangle}
\label{sec:org242c211}

I set this up to tangle the init org-mode file into the actual Emacs
init file as soon as I save it.

\begin{verbatim}
(defun tangle-init ()
  "If the current buffer is 'init.org' the code-blocks are tangled,
and the tangled file is compiled."
  (when (equal (buffer-file-name)
               (expand-file-name "~/Emacs/fengxia.org"))
    ;; Avoid running hooks when tangling.
    (let ((prog-mode-hook nil))
      (org-babel-tangle)
      (byte-compile-file "~/Emacs/fengxia.el"))))

;; auto-tangle hook
(add-hook 'after-save-hook 'tangle-init)
\end{verbatim}

\section{base packages}
\label{sec:org1075415}

There are some packages you'd better load prior to everything else, so
that when other packages are being configured, they are already
available. For example, the .

\subsection{all-the-icons}
\label{sec:orgf73e607}

Want fancy \href{https://github.com/domtronn/all-the-icons.el\#installation}{icons}:
\begin{verbatim}
(use-package all-the-icons
  :ensure)
\end{verbatim}

You would have to run \texttt{M-x all-the-icons-install-fonts=} manually at
least once to install fonts to your system.

\subsection{rainbow-mode}
\label{sec:orgd9a25c9}

Colorize color names and codes in the correct color.

\begin{verbatim}
(use-package rainbow-mode
  :ensure t
  :delight)
\end{verbatim}
\subsection{Hydra}
\label{sec:org19b8c05}
\begin{verbatim}
(use-package hydra
  :ensure t)
\end{verbatim}
\subsection{whichkey}
\label{sec:org3eae559}

Give me a hint when I'm entering a keybinding:
\begin{verbatim}
(use-package which-key
  :ensure
  :config
  (which-key-setup-side-window-right))
(which-key-mode)
\end{verbatim}
\section{global stuff}
\label{sec:org3d53629}

Some global settings such as line number. Well, just about everything
of emacs are global in a sense, say, a package, will affect the look
and behavior when loaded. Even though the mode could be refined to be
loaded only for some file pattern, but hey, the fun is about loading
these funky modes, and with them, a million funky keybinding combos to
remember.

So here, just some obvious value settings. If I find some to be more
topic specific, I will move them into that topic's section instead.

\subsection{by packages}
\label{sec:org8960995}

These are achieved by using someone's package.

\subsubsection{UTF-8}
\label{sec:org1e1157b}

Make Emacs request UTF-8 first when pasting stuff

\begin{verbatim}
(use-package unicode-escape
  :ensure t
  :init
  (setq x-select-request-type '(UTF8_STRING COMPOUND_TEXT TEXT STRING)))
(set-language-environment "UTF-8")
\end{verbatim}

\subsubsection{shell env}
\label{sec:org209f78f}

\begin{verbatim}
(use-package exec-path-from-shell
  :ensure
  :config
  (exec-path-from-shell-initialize))
\end{verbatim}
\subsection{UTF-8 env}
\label{sec:org9f83a1e}
\begin{verbatim}
(prefer-coding-system 'utf-8)

(setenv "LANG" "en_US.UTF-8")
(setenv "LC_ALL" "en_US.UTF-8")
(setenv "LC_CTYPE" "en_US.UTF-8")
\end{verbatim}
\subsection{browser (default: chrome)}
\label{sec:org2521a0b}

I like Chrome. Period.

\begin{verbatim}
(setq browse-url-generic-program (executable-find "google-chrome")
  browse-url-browser-function 'browse-url-generic)
\end{verbatim}

\subsection{emacs server (default: off)}
\label{sec:org44eb461}

Start the background server, so we can use emacsclient.

\begin{verbatim}
(server-start)
\end{verbatim}

\subsection{newline (only Unix wanted)}
\label{sec:org519f433}

This should automatically convert any files with dos or Mac line
endings into Unix style ones. Code found \href{https://www.emacswiki.org/emacs/EndOfLineTips}{here}.

\begin{verbatim}
(defun no-junk-please-we-are-unixish ()
  (let ((coding-str (symbol-name buffer-file-coding-system)))
    (when (string-match "-\\(?:dos\\|mac\\)$" coding-str)
      (set-buffer-file-coding-system 'unix))))

(add-hook 'find-file-hook 'no-junk-please-we-are-unixish)
\end{verbatim}

\subsection{auto revert}
\label{sec:org74258a0}

Use \texttt{auto-revert}, which reloads a file if it's updated on disk and not
modified in the buffer.

\begin{verbatim}
(global-auto-revert-mode 1)
(put 'upcase-region 'disabled nil)
(put 'narrow-to-region 'disabled nil)
\end{verbatim}

\subsection{yes-or-no}
\label{sec:org9ec6b61}

Change all prompts to y or n:

\begin{verbatim}
(fset 'yes-or-no-p 'y-or-n-p)
\end{verbatim}

\subsection{hide menu bar \& toolbar}
\label{sec:org603270b}
Using i3 is forcing me to use keyboard.

\begin{verbatim}
(menu-bar-mode -1)
(toggle-scroll-bar -1)
(tool-bar-mode -1)
(blink-cursor-mode -1)
\end{verbatim}
\subsection{alternate key mappings}
\label{sec:org08dfc72}

Letting one enter chars that are otherwise difficult in e.g. the
minibuffer.

\begin{verbatim}
(global-set-key (kbd "C-m") 'newline-and-indent)
(global-set-key (kbd "C-j") 'newline)
(global-set-key [delete] 'delete-char)
(global-set-key [kp-delete] 'delete-char)
\end{verbatim}
\subsection{macros (default: off)}
\label{sec:orgca7034a}
\begin{verbatim}
(global-set-key [f3] 'start-kbd-macro)
(global-set-key [f4] 'end-kbd-macro)
(global-set-key [f5] 'call-last-kbd-macro)
\end{verbatim}
\subsection{linum}
\label{sec:org09d3715}

For now, I'm doing it globally.

\begin{verbatim}
(global-display-line-numbers-mode t)
\end{verbatim}


Yes I like having line numbers, but turnning it on globally makes some
buffers look strange. So let's limit it to the ones that I think
brings value. \textbf{Note} that the ones I skip are:

\begin{enumerate}
\item mu4e-compose-mode: when writing email, it's better not to count for line num.
\item markdown: for the same reason. I'm writing.
\end{enumerate}

\begin{verbatim}
(add-hook 'c-mode-common-hook 'display-line-numbers-mode)
(add-hook 'org-mode-hook 'display-line-numbers-mode)
(add-hook 'elpy-mode-hook 'display-line-numbers-mode)
(add-hook 'web-mode-hook 'display-line-numbers-mode)
(add-hook 'js2-mode-hook 'display-line-numbers-mode)
(add-hook 'yaml-mode-hook 'display-line-numbers-mode)
(add-hook 'json-mode-hook 'display-line-numbers-mode)
(add-hook 'java-mode-hook 'display-line-numbers-mode)
\end{verbatim}

\section{font, theme}
\label{sec:orgef6d1b6}

The whole point of using emacs is that I like the user experience, and
a big part of it is the color and look. There are too many ways to
tweak it. So I'll try not to run wild on this one. Most are inherited
from the original post, and I added some while playing with this
setting. Enjoy \textasciitilde{}\textasciitilde{}

\subsection{by packages}
\label{sec:org6dc7d1f}

\subsubsection{sublime themes (default: spolsky)}
\label{sec:org26f6f09}

Loading a theme I like.

\begin{verbatim}
  (use-package sublime-themes
    :ensure
    :config)
(add-hook 'after-init-hook (lambda () (load-theme 'spolsky t)))
\end{verbatim}

\subsubsection{mode lines}
\label{sec:orgb0e7bed}
\begin{enumerate}
\item doom-modeline
\label{sec:orgd497039}
\begin{verbatim}
(use-package doom-modeline
  :ensure t
  :init (doom-modeline-mode 1))
\end{verbatim}
\item remove some modelines
\label{sec:org5a2394a}
\begin{verbatim}
(use-package eldoc
  :delight)
\end{verbatim}
\item nyan-mode
\label{sec:orgb018e9d}
\begin{verbatim}
(use-package nyan-mode
  :ensure t
  :bind ("C-M-x n" . 'nyan-mode))
\end{verbatim}
\end{enumerate}
\subsubsection{delight}
\label{sec:orgf5bc969}
Package to remove some info from the mode-line for minor-modes.
\begin{verbatim}
(use-package delight
  :ensure t)
\end{verbatim}
\subsubsection{multiple-cursors}
\label{sec:org927c3c6}

Configure the shortcuts for multiple cursors.

\begin{verbatim}
(use-package multiple-cursors
  :ensure t
  :bind (("C-S-c C-S-c" . 'mc/edit-lines)
         ("C->" . 'mc/mark-next-like-this)
         ("C-<" . 'mc/mark-previous-like-this)
         ("C-c C->" . 'mc/mark-all-like-this)))
\end{verbatim}
\subsubsection{dimmer}
\label{sec:org6bf3dd9}

This will dim the buffer that is not the current. Sort of a visual
cue. However, I found that it can be ugly depending the theme.

\begin{verbatim}
(use-package dimmer
  :ensure
  :config
  (dimmer-configure-which-key)
  (dimmer-configure-helm))
(dimmer-mode t)
\end{verbatim}

\subsubsection{highlight indent}
\label{sec:org7520ccd}
\begin{verbatim}
(use-package highlight-indent-guides
:ensure
:config
(setq highlight-indent-guides-method 'character))
(add-hook 'prog-mode-hook 'highlight-indent-guides-mode)
\end{verbatim}
\subsection{fontlock}
\label{sec:org1933d98}

This gets the font coloring switched on for all buffers.

I have encountered a strange case when a mal-formatted Java file
caused Emacs to crash. After many research, the remedy is to use
\href{https://github.com/jhipster/prettier-java}{prettier-java} to reformat this file first, then emacs is happy.

\begin{verbatim}
(global-font-lock-mode t)
\end{verbatim}

\subsection{faces}
\label{sec:org007a619}

This makes some of the faces a bit more contrasted.

\begin{verbatim}
;; faces for general region highlighting zenburn is too low-key.
(custom-set-faces
 '(highlight ((t (:background "forest green"))))
 '(region ((t (:background "forest green")))))
\end{verbatim}


\subsection{be quiet}
\label{sec:orgd7113e0}
Remove bell and dings.

\begin{verbatim}
(setq ring-bell-function
      '(lambda ()
         (message "The answer is 42...")))
(setq echo-keystrokes 0.1 use-dialog-box nil visible-bell t)
\end{verbatim}
\subsection{In terminal mode}
\label{sec:org5046155}
\begin{verbatim}
(when (display-graphic-p)
  (set-background-color "#ffffff")
  (set-foreground-color "#141312"))
\end{verbatim}
\subsection{In X11 mode: mouse and window title}
\label{sec:orgf4a34b9}
\begin{verbatim}
(setq frame-title-format "emacs @ %b - %f")
(when window-system
  (mouse-wheel-mode)  ;; enable wheelmouse support by default
  (set-selection-coding-system 'compound-text-with-extensions))
\end{verbatim}
\subsection{dynamic cursor colors}
\label{sec:org7e05030}

The cursor is displayed in different colors, depending on overwrite or
insert mode.

\begin{verbatim}
(setq hcz-set-cursor-color-color "")
(setq hcz-set-cursor-color-buffer "")

(defun hcz-set-cursor-color-according-to-mode ()
  "change cursor color according to some minor modes."
  ;; set-cursor-color is somewhat costly, so we only call it when needed:
  (let ((color
         (if buffer-read-only "orange"
           (if overwrite-mode "red"
             "green"))))
    (unless (and
             (string= color hcz-set-cursor-color-color)
             (string= (buffer-name) hcz-set-cursor-color-buffer))
      (set-cursor-color (setq hcz-set-cursor-color-color color))
      (setq hcz-set-cursor-color-buffer (buffer-name)))))

(add-hook 'post-command-hook 'hcz-set-cursor-color-according-to-mode)
\end{verbatim}
\section{the big Org}
\label{sec:org2f6f7f4}

Org-mode is, overwhelming! It can do a lot, and it takes a long time
for me to understand what it does (and what it doesn't). Part of this
config in org mode is just the way to force myself to learn org mdoe
and write things in org mode. I haven't yet taken full advantage of
its TODO capability. Well, one day.

\subsection{init}
\label{sec:org0a95cb4}

If variable \texttt{org-directory} is not set yet, map it to my home's
files. You may set this in the \texttt{\textasciitilde{}/.emacs} to another value,
e.g. \texttt{(setq org-directory "/ssh:fleury@machine.site.com:OrgFiles")}

\subsubsection{{\bfseries\sffamily NEXT} This does not seem to work, check out doc about \href{https://stackoverflow.com/questions/3806423/how-can-i-get-a-variables-initial-value-in-elisp}{defcustom}}
\label{sec:orga277f21}
\begin{verbatim}
(use-package org
  :ensure nil
  :delight org-mode
  :config
  (setq org-startup-indented t)
  (if (not (boundp 'org-directory))
      (setq org-directory "~/org"))
  (add-hook 'org-mode-hook #'(lambda ()
                               (visual-line-mode)
                               (org-indent-mode))))
\end{verbatim}

\subsection{others}
\label{sec:orgd8f99fa}

Don't know what they belong to. Just stuck them here. There are some functions used by the following code. So unfortunately this section must comes in early.

\subsubsection{snippets found online}
\label{sec:orgf5a30cb}

Some helper snippets found online.

\begin{enumerate}
\item Open remote org dir
\label{sec:org0e098f5}

In your \texttt{.emacs} just add this to configure the location:

\begin{verbatim}
(setq remote-org-directory "/ssh:fleury@my.hostname.com:OrgFiles")
\end{verbatim}

Then you can use the keyboard shortcut to open that dir.

\begin{verbatim}
(defcustom remote-org-directory "~/OrgFiles"
  "Location of remove OrgFile directory, should you have one."
  :type 'string
  :group 'paf)
(defun paf/open-remote-org-directory ()
  (interactive)
  (find-file remote-org-directory))

(global-set-key (kbd "C-M-x r o") 'paf/open-remote-org-directory)
\end{verbatim}

\item Org-relative file function
\label{sec:org9bcc637}

\begin{verbatim}
(defun org-relative-file (filename)
  "Compute an expanded absolute file path for org files"
  (expand-file-name filename org-directory))
\end{verbatim}
\item Adjust tags on the right
\label{sec:org2108d83}

Dynamically adjust tag position \href{https://orgmode.org/worg/org-hacks.html\#org0560357}{source on worg}

\begin{verbatim}
(defun ba/org-adjust-tags-column-reset-tags ()
  "In org-mode buffers it will reset tag position according to
`org-tags-column'."
  (when (and
         (not (string= (buffer-name) "*Remember*"))
         (eql major-mode 'org-mode))
    (let ((b-m-p (buffer-modified-p)))
      (condition-case nil
          (save-excursion
            (goto-char (point-min))
            (command-execute 'outline-next-visible-heading)
            ;; disable (message) that org-set-tags generates
            (cl-letf (((symbol-function 'message) #'format))
              (org-set-tags 1 t))
            (set-buffer-modified-p b-m-p))
        (error nil)))))

(defun ba/org-adjust-tags-column-now ()
  "Right-adjust `org-tags-column' value, then reset tag position."
  (set (make-local-variable 'org-tags-column)
       (- (- (window-width) (length org-ellipsis))))
  (ba/org-adjust-tags-column-reset-tags))

(defun ba/org-adjust-tags-column-maybe ()
  "If `ba/org-adjust-tags-column' is set to non-nil, adjust tags."
  (when ba/org-adjust-tags-column
    (ba/org-adjust-tags-column-now)))

(defun ba/org-adjust-tags-column-before-save ()
  "Tags need to be left-adjusted when saving."
  (when ba/org-adjust-tags-column
     (setq org-tags-column 1)
     (ba/org-adjust-tags-column-reset-tags)))

(defun ba/org-adjust-tags-column-after-save ()
  "Revert left-adjusted tag position done by before-save hook."
  (ba/org-adjust-tags-column-maybe)
  (set-buffer-modified-p nil))

;; between invoking org-refile and displaying the prompt (which
;; triggers window-configuration-change-hook) tags might adjust,
;; which invalidates the org-refile cache
(defadvice org-refile (around org-refile-disable-adjust-tags)
  "Disable dynamically adjusting tags"
  (let ((ba/org-adjust-tags-column nil))
    ad-do-it))
(ad-activate 'org-refile)

;; Now set it up
(setq ba/org-adjust-tags-column t)
;; automatically align tags on right-hand side
;; TODO(fleury): Does not seem to work as of 2017/12/18
;; Seems to work again 2018/11/01
(add-hook 'window-configuration-change-hook
          'ba/org-adjust-tags-column-maybe)
(add-hook 'before-save-hook 'ba/org-adjust-tags-column-before-save)
(add-hook 'after-save-hook 'ba/org-adjust-tags-column-after-save)
(add-hook 'org-agenda-mode-hook (lambda ()
                                  (setq org-agenda-tags-column (- (window-width)))))
\end{verbatim}

\begin{enumerate}
\item {\bfseries\sffamily TODO} Update \texttt{org-set-tags-to}
\label{sec:orgc9f054b}
\href{https://orgmode.org/worg/doc.html\#org-set-tags-to}{\texttt{org-set-tags-to}} is gone, and \texttt{org-set-tags} with > 1 args is not working.
Not sure what to replace it with though\ldots{}
\end{enumerate}

\item Preserve structure in archives
\label{sec:orgee0ab90}

Make sure archiving preserves the same tree structure, including when
archiving subtrees.  \href{https://orgmode.org/worg/org-hacks.html\#org4265b4c}{source on worg}

\begin{verbatim}
(defun my-org-inherited-no-file-tags ()
  (let ((tags (org-entry-get nil "ALLTAGS" 'selective))
        (ltags (org-entry-get nil "TAGS")))
    (mapc (lambda (tag)
            (setq tags
                  (replace-regexp-in-string (concat tag ":") "" tags)))
          (append org-file-tags (when ltags (split-string ltags ":" t))))
    (if (string= ":" tags) nil tags)))
\end{verbatim}

This used to work, but \texttt{org-extract-archive-file} is no longer defined.

\begin{verbatim}
(defadvice org-archive-subtree
    (around my-org-archive-subtree-low-level activate)
  (let ((tags (my-org-inherited-no-file-tags))
        (org-archive-location
         (if (save-excursion (org-back-to-heading)
                             (> (org-outline-level) 1))
             (concat (car (split-string org-archive-location "::"))
                     "::* "
                     (car (org-get-outline-path)))
           org-archive-location)))
    ad-do-it
    (with-current-buffer (find-file-noselect (org-extract-archive-file))
      (save-excursion
        (while (org-up-heading-safe))
        (org-set-tags tags)))))
\end{verbatim}
\item Properties collector (default: off)
\label{sec:org8098378}

Collect properties into tables. See documentation in the file.

\begin{verbatim}
(load-file "~/Emacs/org-collector.el")
\end{verbatim}
\item access org file remotely via SSH
\label{sec:org2a8ff13}

Let's bind this to a key, so I can open remote dirs. I suually put
this in my \texttt{.emacs} as it is host- and user-specific.

\begin{verbatim}
(defun paf/open-remote-org-dir ()
  (interactive)
  (dired "/ssh:remote.host.com:org"))

(global-set-key (kbd "C-M-x r o") 'paf/open-remote-org-dir)
\end{verbatim}

\item bash command
\label{sec:org826d2a2}
\begin{verbatim}
(setq org-babel-sh-command "bash")
\end{verbatim}

\item OrgRoam templates
\label{sec:orgd7752ba}

\begin{verbatim}
(setq org-roam-capture-templates
      `(("m" "Meeting" entry (function org-roam--capture-get-point)
             "* %?\n%U\n%^{with}\n"
             :file-name "meeting/%<%Y%m%d%H%M%S>-${slug}"
             :head "#+title: ${title}\n#+roam_tags: %^{with}\n\n"
             )))

\end{verbatim}
\end{enumerate}
\subsubsection{by packages}
\label{sec:org3a049c8}
\begin{enumerate}
\item org-protocol
\label{sec:org60621f7}

Let other tools use emacs client to interact

\begin{verbatim}
(require 'org-protocol)
\end{verbatim}

\item org-roam
\label{sec:org89906ea}
My cheat sheet for \texttt{org-roam}

All keys prefixed with \texttt{C-c n}

\begin{center}
\begin{tabular}{lc}
\hline
Function & \texttt{C-c n <key>}\\
\hline
Toggle side panel & l\\
\hline
Find/create & f\\
Insert link & i\\
Capture & c\\
\hline
Graph & g\\
Switch to buffer & b\\
\hline
\end{tabular}
\end{center}


\begin{verbatim}
(use-package org-roam
  :ensure t
  :hook (after-init . org-roam-mode)
  :init (setq org-roam-directory
              (org-relative-file "OrgRoam"))
  :bind (:map org-roam-mode-map
              (("C-c n l" . org-roam)
               ("C-c n b" . org-roam-switch-to-buffer)
               ("C-c n f" . org-roam-find-file)
               ("C-c n c" . org-roam-capture)
               ("C-c n g" . org-roam-graph))
         :map org-mode-map
              (("C-c n i" . org-roam-insert))))

(use-package company-org-roam
  :ensure t
  :after org-roam)
\end{verbatim}

EmacSQL will need to get its C-binary compiled, and needs supporting
tools. Note that 'tcc' for Termux seems not complete enough for the
job.

\item org-board
\label{sec:org540eae2}
Archive entire sites locally with `wget`.

\begin{verbatim}
(use-package org-board
  :ensure t
  :config
  (global-set-key (kbd "C-c o") org-board-keymap))
\end{verbatim}

\item iimage (M-I)
\label{sec:org18af3e8}

Make the display of images a simple key-stroke away.

\begin{verbatim}
(defun paf/org-toggle-iimage-in-org ()
  "display images in your org file"
  (interactive)
  (if (face-underline-p 'org-link)
      (set-face-underline 'org-link nil)
    (set-face-underline 'org-link t))
  (iimage-mode 'toggle))

(use-package iimage
  :config
  (add-to-list 'iimage-mode-image-regex-alist
               (cons (concat "\\[\\[file:\\(~?" iimage-mode-image-filename-regex
                             "\\)\\]")  1))
  (add-hook 'org-mode-hook (lambda ()
                             ;; display images
                             (local-set-key "\M-I" 'paf/org-toggle-iimage-in-org)
                            )))
\end{verbatim}
\end{enumerate}

\subsection{key mappings}
\label{sec:org47e316d}

\begin{verbatim}
(global-set-key (kbd "C-c l") 'org-store-link)
(global-set-key (kbd "C-c c") 'org-capture)
(global-set-key (kbd "C-c a") 'org-agenda)
(global-set-key (kbd "C-c b") 'org-iswitchb)

(add-hook 'org-mode-hook
          (lambda ()
            (local-set-key (kbd "C-<up>") 'org-move-subtree-up)
            (local-set-key (kbd "C-<down>") 'org-move-subtree-down)
            (local-set-key (kbd "C-c l") 'org-store-link)
            (local-set-key (kbd "C-c C-l") 'org-insert-link)))

\end{verbatim}
\subsection{display settings}
\label{sec:org28630a0}
Some config for display. Some of these are borrowed from \href{https://zzamboni.org/post/beautifying-org-mode-in-emacs/}{here}:

\begin{verbatim}
(setq org-hide-leading-stars t)
(setq org-log-done t)
(setq org-startup-indented t)
(setq org-startup-folded t)
(setq org-ellipsis "...")
(setq org-hide-emphasis-markers t)
\end{verbatim}

\subsubsection{org-bullets}
\label{sec:org96e500a}
\begin{verbatim}
(use-package org-bullets
  :ensure
  :config)
(add-hook 'org-mode-hook (lambda () (org-bullets-mode 1)))
\end{verbatim}
\subsection{writing stuff}
\label{sec:org4f11a5a}

Part 1, writing stuff such as taking notes.

\subsubsection{by packages}
\label{sec:org783d09d}
\begin{enumerate}
\item Zetteldeft
\label{sec:org87d1098}

This is a note-taking packages inspired by the principles of the
\href{https://zettelkasten.de/}{Zettelkasten.}

\begin{verbatim}
(use-package deft
  :ensure t)
(use-package avy
  :ensure t)

(use-package zetteldeft
  :ensure t
  :after (org deft avy)

  :config
  (setq deft-extensions '("org" "md" "txt"))
  (setq deft-directory (org-relative-file "Zettelkasten"))
  (setq deft-recursive t)

  :bind (("C-c z d" . deft)
         ("C-c z D" . zetteldeft-deft-new-search)
         ("C-c z R" . deft-refresh)
         ("C-c z s" . zetteldeft-search-at-point)
         ("C-c z c" . zetteldeft-search-current-id)
         ("C-c z f" . zetteldeft-follow-link)
         ("C-c z F" . zetteldeft-avy-file-search-ace-window)
         ("C-c z l" . zetteldeft-avy-link-search)
         ("C-c z t" . zetteldeft-avy-tag-search)
         ("C-c z T" . zetteldeft-tag-buffer)
         ("C-c z i" . zetteldeft-find-file-id-insert)
         ("C-c z I" . zetteldeft-find-file-full-title-insert)
         ("C-c z o" . zetteldeft-find-file)
         ("C-c z n" . zetteldeft-new-file)
         ("C-c z N" . zetteldeft-new-file-and-link)
         ("C-c z r" . zetteldeft-file-rename))
)
\end{verbatim}

\item plant-uml
\label{sec:org9676ac2}

Tell where PlantUML is to be found. This needs to be downloaded and
installed separately, see the \href{http://plantuml.com/}{PlantUML website}.

\begin{verbatim}
(use-package plantuml-mode
 :ensure t
 :config
  (setq plantuml-jar-path "~/workspace/me/myblog/content/downloads/plantuml.jar")
  (setq org-plantuml-jar-path "~/workspace/me/myblog/content/downloads/plantuml.jar")
  ;; Let us edit PlantUML snippets in plantuml-mode within orgmode
  (add-to-list 'org-src-lang-modes '("plantuml" . plantuml))
  ;; make it load this language (for export ?)
  (org-babel-do-load-languages 'org-babel-load-languages '((plantuml . t)))
  ;; Enable plantuml-mode for PlantUML files
  (add-to-list 'auto-mode-alist '("\\.plantuml\\'" . plantuml-mode)))
\end{verbatim}
\end{enumerate}

\subsubsection{org-link-abbrev}
\label{sec:org9350970}

This lets one write links as e.g. [ [b:123457] ]

\begin{verbatim}
(setq org-link-abbrev-alist
      '(("b" . "http://b/")
        ("go" . "http://go/")
        ("cl" . "http://cr/")))
\end{verbatim}
\subsection{export}
\label{sec:org5ac5bec}

Part 2, exporting.

This is big deal. It took me a while to learn org, and even right now
I still don't know how to use it for schedule management. This feels
like latex, it's wonderful, but not common among non-org-mode folks.

Add a few formats to the export functionality of org-mode.
\subsubsection{org-babel}
\label{sec:orgfaac233}

What kind of code block languages do I need

\begin{verbatim}
(setq org-confirm-babel-evaluate 'nil) ; Don't ask before executing

(org-babel-do-load-languages
 'org-babel-load-languages
 '(
   (R . t)
   (dot . t)
   (emacs-lisp . t)
   (gnuplot . t)
   (python . t)
   (ledger . t)
   ;;(sh . t)
   (latex . t)
   (shell . t)
  ))
\end{verbatim}

\subsubsection{markdown}
\label{sec:org5724dba}
\begin{verbatim}
(use-package ox-md
  :defer)
\end{verbatim}
\subsubsection{beamer}
\label{sec:org527797a}
\begin{verbatim}
(use-package ox-beamer
  :defer)
\end{verbatim}
\subsubsection{org-reveal}
\label{sec:org6c6b05c}

You need to install \texttt{reveal.js} offline, then specify its path here.
\begin{verbatim}
(use-package ox-reveal
  :ensure t
  :after (htmlize)
  :config
  (setq org-reveal-root (expand-file-name "~/reveal.js")))

(use-package htmlize
  :ensure t)
\end{verbatim}
\subsubsection{odt}
\label{sec:org2bb1150}
\begin{verbatim}
(use-package ox-odt
  :defer)
\end{verbatim}
\subsubsection{taskjuggler}
\label{sec:org0c2cf98}
\begin{verbatim}
(use-package ox-taskjuggler
  :defer)
\end{verbatim}
\subsubsection{confluence}
\label{sec:org5c9bab8}
\begin{verbatim}
(use-package ox-confluence
  :defer)
\end{verbatim}

\subsection{managing life (aka. agenda/todo)}
\label{sec:org43dfb07}

Part 3 of org, managing TODOs.

\subsubsection{by packages}
\label{sec:org454bc3a}
\begin{enumerate}
\item org-super-agenda
\label{sec:org76c6209}

This enables a more fine-grained filtering of the agenda items.

\begin{verbatim}
(use-package org-super-agenda
  :ensure t
  :config
  (org-super-agenda-mode t))
\end{verbatim}
\item org-clock-convenience
\label{sec:org3e61d5b}
\begin{verbatim}
(use-package org-clock-convenience
  :ensure t
  :bind (:map org-agenda-mode-map
           ("<S-right>" . org-clock-convenience-timestamp-up)
           ("<S-left>" . org-clock-convenience-timestamp-down)
           ("[" . org-clock-convenience-fill-gap)
           ("]" . org-clock-convenience-fill-gap-both)))
\end{verbatim}
\item org-habit
\label{sec:orgf7714fc}
\begin{verbatim}
(use-package org-habit
  :delight
  :config
  (setq org-habit-graph-column 38)
  (setq org-habit-preceding-days 35)
  (setq org-habit-following-days 10)
  (setq org-habit-show-habits-only-for-today nil))
\end{verbatim}
\item org-secretary
\label{sec:orgc69d878}

This package is good, but it does not do it simply. I re-modeled it
somewhat below.

\begin{verbatim}
(use-package org-secretary
  :ensure org-plus-contrib
  :config
  (setq org-sec-me "feng")
  (setq org-tag-alist '(("PRJ" . ?p)
                        ("DESIGNDOC" . ?D)
                        ("Milestone" . ?m)
                        ("DESK" . ?d)
                        ("HOME" . ?h)
                        ("VC" . ?v))))
\end{verbatim}

This is my version of the org-secretary
\begin{verbatim}
(use-package paf-secretary
  :load-path "~/Emacs"
  :bind (("\C-cw" . paf-sec-set-with)
         ("\C-cW" . paf-sec-set-where)
         ("\C-cj" . paf-sec-tag-entry))
  :config
  (setq paf-sec-me "paf")
  (setq org-tag-alist '(("PRJ" . ?p)
                        ("DESIGNDOC" . ?D)
                        ("Milestone" . ?m)
                        ("DESK" . ?d)
                        ("HOME" . ?h)
                        ("VC" . ?v))))
\end{verbatim}
\item org-duration
\label{sec:org8cdbf63}
\begin{verbatim}
(use-package org-duration
  :config
  (setq org-duration-units
        `(("min" . 1)
          ("h" . 60)
          ("d" . ,(* 60 8))
          ("w" . ,(* 60 8 5))
          ("m" . ,(* 60 8 5 4))
          ("y" . ,(* 60 8 5 4 10)))
        )
  (org-duration-set-regexps))
\end{verbatim}
\end{enumerate}
\subsubsection{org TODO keywords}
\label{sec:orgd8f0981}

\begin{verbatim}
(setq org-todo-keywords
      '((sequence "TODO(t!)" "NEXT(n!)" "STARTED(s!)" "WAITING(w!)" "AI(a!)" "|" "DONE(d!)" "CANCELLED(C@)" "DEFERRED(D@)" "SOMEDAY(S!)" "FAILED(F!)" "REFILED(R!)")
        (sequence "APPLIED(A!)" "WAITING(w!)" "ACCEPTED" "|" "REJECTED" "PUBLISHED")
        (sequence "TASK(m!)" "ACTIVE" "|" "DONE(d!)" "CANCELLED(C@)" )))

(setq org-tags-exclude-from-inheritance '("PRJ" "REGULAR")
      org-use-property-inheritance '("PRIORITY")
      org-stuck-projects '("+PRJ/-DONE-CANCELLED"
                           ;; it is considered stuck if there is no next action
                           (;"TODO"
                            "NEXT" "STARTED" "TASK") ()))

(setq org-todo-keyword-faces
      '(
        ("TODO" . (:foreground "purple" :weight bold))
        ("TASK" . (:foreground "steelblue" :weight bold))
        ("NEXT" . (:foreground "red" :weight bold))
        ("STARTED" . (:foreground "green" :weight bold))
        ("WAITING" . (:foreground "orange" :weight bold))
        ("FLAG_GATED" . (:foreground "orange" :weight bold))
        ("SOMEDAY" . (:foreground "steelblue" :weight bold))
        ("MAYBE" . (:foreground "steelblue" :weight bold))
        ("AI" . (:foreground "red" :weight bold))
        ("NEW" . (:foreground "orange" :weight bold))
        ("RUNNING" . (:foreground "orange" :weight bold))
        ("WORKED" . (:foreground "green" :weight bold))
        ("FAILED" . (:foreground "red" :weight bold))
        ("REFILED" . (:foreground "gray"))
        ;; For publications
        ("APPLIED" . (:foreground "orange" :weight bold))
        ("ACCEPTED" . (:foreground "orange" :weight bold))
        ("REJECTED" . (:foreground "red" :weight bold))
        ("PUBLISHED" . (:foreground "green" :weight bold))
        ;; Other stuff
        ("ACTIVE" . (:foreground "darkgreen" :weight bold))
        ))
\end{verbatim}

\subsubsection{capture \& refile}
\label{sec:orgbd59a98}

Capture and refile stuff, with some templates that I think are useful.

Very nice post on how to get capture templats from a file: \href{https://joshrollinswrites.com/help-desk-head-desk/org-capture-in-files/}{Org-capture
in Files}.

\begin{verbatim}
(setq org-default-notes-file (org-relative-file "Inbox.org"))

(setq org-capture-templates
      `(("t" "Task"
         entry (file+headline ,(org-relative-file "Inbox.org") "Tasks")
         "* TODO %?\n%U\n\n%x"
         :clock-resume t)
        ;;
        ("i" "Idea"
         entry (file+headline ,(org-relative-file "Inbox.org") "Ideas")
         "* SOMEDAY %?\n%U\n\n%x"
         :clock-resume t)
        ;;
        ("m" "Meeting"
         entry (file+headline ,(org-relative-file "Inbox.org") "Meetings")
         "* %?  :MTG:\n%U\n%^{with}p"
         :clock-in t
         :clock-resume t)
        ;;
        ("s" "Stand-up"
         entry (file+headline ,(org-relative-file "Inbox.org") "Meetings")
         "* Stand-up  :MTG:\n%U\n\n%?"
         :clock-in t
         :clock-resume t)
        ;;
        ("1" "1:1"
         entry (file+headline ,(org-relative-file "Inbox.org") "Meetings")
         "* 1:1 %^{With}  :MTG:\n%U\n:PROPERTIES:\n:with: %\\1\n:END:\n\n%?"
         :clock-in t
         :clock-resume t)
        ;;
        ("p" "Talking Point"
         entry (file+headline ,(org-relative-file "refile.org") "Talking Points")
         "* %?  :TALK:\n%U\n%^{dowith}p"
         :clock-keep t)
        ;;
        ("j" "Journal"
         entry (file+olp+datetree ,(org-relative-file "journal.org"))
         "* %?\n%U"
         :clock-in t
         :clock-resume t
         :kill-buffer t)))

;; show up to 2 levels for refile targets, in all agenda files
(setq org-refile-targets '((org-agenda-files . (:maxlevel . 2))))
(setq org-log-refile t)  ;; will add timestamp when refiled.

;; from: http://doc.norang.ca/org-mode.html
;; Exclude DONE state tasks from refile targets
(defun bh/verify-refile-target ()
  "Exclude todo keywords with a done state from refile targets"
  (not (member (nth 2 (org-heading-components)) org-done-keywords)))
(setq org-refile-target-verify-function 'bh/verify-refile-target)
\end{verbatim}
\subsubsection{task tracking}
\label{sec:org303b0f9}

Track task dependencies, and dim them in the agenda.

\begin{verbatim}
(setq org-enforce-todo-dependencies t)
(setq org-agenda-dim-blocked-tasks 'invisible)
\end{verbatim}
\subsubsection{effort \& columns mode}
\label{sec:org64e6d54}

\begin{verbatim}
(setq org-global-properties
      '(("Effort_ALL". "0 0:10 0:30 1:00 2:00 4:00 8:00 16:00")))
(setq org-columns-default-format
      "%TODO %30ITEM %3PRIORITY %6Effort{:} %10DEADLINE")
\end{verbatim}

\subsubsection{shortcut to open first agenda file}
\label{sec:org9b3118a}

F12 open the first agenda file

\begin{verbatim}
(defun org-get-first-agenda-file ()
  (interactive)
  (find-file (elt org-agenda-files 0)))
(global-set-key [f12] 'org-get-first-agenda-file)
; F12 on Mac OSX displays the dashboard....
(global-set-key [C-f12] 'org-get-first-agenda-file)
\end{verbatim}

\subsubsection{org-agenda}
\label{sec:orge0fe785}
\begin{enumerate}
\item views
\label{sec:org885ad2a}
\begin{verbatim}
(setq org-agenda-custom-commands
      '(("t" "Hot Today" ((agenda "" ((org-agenda-span 'day)))
                          (tags-todo "-with={.+}/WAITING")
                          (tags-todo "-with={.+}+TODO=\"STARTED\"")
                          (tags-todo "/NEXT")))
        ("T" "Team Today" ((agenda "" ((org-agenda-span 'day)))
                           (tags-todo "with={.+}"
                                    ((org-super-agenda-groups
                                      '((:auto-property "with"))))
                                    )))
        ("r" "Recurring" ((tags "REGULAR")
                          (tags-todo "/WAITING")
                          (tags-todo "TODO=\"STARTED\"")
                          (tags-todo "/NEXT")))
        ("n" "Agenda and all TODO's" ((agenda "")
                                      (alltodo "")))
        ("N" "Next actions" tags-todo "-dowith={.+}/!-TASK-TODO"
         ((org-agenda-todo-ignore-scheduled t)))
        ("h" "Work todos" tags-todo "-dowith={.+}/!-TASK"
         ((org-agenda-todo-ignore-scheduled t)))
        ("H" "All work todos" tags-todo "-personal/!-TASK-CANCELLED"
         ((org-agenda-todo-ignore-scheduled nil)))
        ("A" "Work todos with doat or dowith" tags-todo
         "dowith={.+}/!-TASK"
         ((org-agenda-todo-ignore-scheduled nil)))

        ("p" "Tasks with current WITH and WHERE"
         ((tags-todo (paf-sec-replace-with-where "with={$WITH}" ".+")
                     ((org-agenda-overriding-header
                       (paf-sec-replace-with-where "Tasks with $WITH in $WHERE" "anyone" "any place"))
                      (org-super-agenda-groups
                       '((:name "" :pred paf-sec-limit-to-with-where)
                         (:discard (:anything t)))))
                     )))
        ("j" "TODO dowith and TASK with"
         ((org-sec-with-view "TODO dowith")
          (org-sec-stuck-with-view "TALK with")
          (org-sec-where-view "TODO doat")
          (org-sec-assigned-with-view "TASK with")
          (org-sec-stuck-with-view "STUCK with")
          (todo "STARTED")))
        ("J" "Interactive TODO dowith and TASK with"
         ((org-sec-who-view "TODO dowith")))))

(setq org-agenda-skip-deadline-prewarning-if-scheduled 2)
\end{verbatim}
\item delight
\label{sec:org0d5ea2c}
\begin{verbatim}
(delight 'org-agenda-mode)
\end{verbatim}
\item colors and faces
\label{sec:orgf1b1a27}

Make the calendar day info a bit more visible and contrasted.

\begin{verbatim}
;; Faces to make the calendar more colorful.
(custom-set-faces
 '(org-agenda-current-time ((t (:inherit org-time-grid :foreground "yellow" :weight bold))))
 '(org-agenda-date ((t (:inherit org-agenda-structure :background "pale green" :foreground "black" :weight bold))))
 '(org-agenda-date-weekend ((t (:inherit org-agenda-date :background "light blue" :weight bold)))))
\end{verbatim}
\item now marker
\label{sec:org49b98e7}

A more visible current-time marker in the agenda

\begin{verbatim}
(setq org-agenda-current-time-string ">>>>>>>>>> NOW <<<<<<<<<<")
\end{verbatim}
\item auto-refresh
\label{sec:orgf3a25e9}

\begin{verbatim}
;; will refresh it only if already visible
(run-at-time nil 180 'update-agenda-if-visible)
;;(add-hook 'org-mode-hook
;;          (lambda () (run-at-time nil 180 'kiwon/org-agenda-redo-in-other-window)))
\end{verbatim}

This would open the agenda if any org file was opened. In the end, I
don't like this feature, so it is disabled by not tangling it.

\begin{verbatim}
;; Make this happen only if we open an org file.
(add-hook 'org-mode-hook
          (lambda () (run-with-idle-timer 600 t 'jump-to-org-agenda)))
\end{verbatim}
\item auto-save org files when idle
\label{sec:org5bbf496}

This will save them regularly when the idle for more than a minute.

\begin{verbatim}
(add-hook 'org-mode-hook
          (lambda () (run-with-idle-timer 600 t 'org-save-all-org-buffers)))
\end{verbatim}
\item export
\label{sec:orge6c8f30}

That's the export function to update the agenda view.

\begin{verbatim}
(setq org-agenda-exporter-settings
      '((ps-number-of-columns 2)
        (ps-portrait-mode t)
        (org-agenda-add-entry-text-maxlines 5)
        (htmlize-output-type 'font)))

(defun dmg-org-update-agenda-file (&optional force)
  (interactive)
  (save-excursion
    (save-window-excursion
      (let ((file "~/www/agenda/agenda.html"))
        (org-agenda-list)
        (org-agenda-write file)))))
\end{verbatim}
\item Auto-Refresh Agenda
\label{sec:orgc950ff3}

Refresh org-mode agenda regularly.  \href{https://orgmode.org/worg/org-hacks.html\#orgab827a7}{source on worg} There are two
functions that supposedly do the same.

\begin{verbatim}
(defun kiwon/org-agenda-redo-in-other-window ()
  "Call org-agenda-redo function even in the non-agenda buffer."
  (interactive)
  (let ((agenda-window (get-buffer-window org-agenda-buffer-name t)))
    (when agenda-window
      (with-selected-window agenda-window (org-agenda-redo)))))

(defun update-agenda-if-visible ()
  (interactive)
  (let ((buf (get-buffer "*Org Agenda*"))
        wind)
    (if buf
        (org-agenda-redo))))
\end{verbatim}
\item Display Agenda when idle
\label{sec:org2c53479}

Show the agenda when emacs left idle.  \href{https://orgmode.org/worg/org-hacks.html\#orgaea636d}{source on worg}

\begin{verbatim}
(defun jump-to-org-agenda ()
  (interactive)
  (let ((buf (get-buffer "*Org Agenda*"))
        wind)
    (if buf
        (if (setq wind (get-buffer-window buf))
            (select-window wind)
          (if (called-interactively-p 'any)
              (progn
                (select-window (display-buffer buf t t))
                (org-fit-window-to-buffer)
                (org-agenda-redo)
                )
            (with-selected-window (display-buffer buf)
              (org-fit-window-to-buffer)
              ;;(org-agenda-redo)
              )))
      (call-interactively 'org-agenda-list)))
  ;;(let ((buf (get-buffer "*Calendar*")))
  ;;  (unless (get-buffer-window buf)
  ;;    (org-agenda-goto-calendar)))
  )
\end{verbatim}
\item Display location in agenda
\label{sec:org08a2277}

From some help on \href{https://emacs.stackexchange.com/questions/26249/customize-text-after-task-in-custom-org-agenda-view}{this page} I think this could work:

\begin{verbatim}
(defun paf/org-agenda-get-location()
  "Gets the value of the LOCATION property"
  (let ((loc (org-entry-get (point) "LOCATION")))
    (if (> (length loc) 0)
        loc
      "")))
\end{verbatim}

Also, to set this after org-mode has loaded (\href{https://emacs.stackexchange.com/questions/19091/how-to-set-org-agenda-prefix-format-before-org-agenda-starts}{see here}):
\begin{verbatim}
(with-eval-after-load 'org-agenda
  (add-to-list 'org-agenda-prefix-format
               '(agenda . "  %-12:c%?-12t %(paf/org-agenda-get-location)% s"))
\end{verbatim}
\end{enumerate}
\subsubsection{org-clock properties}
\label{sec:orgf17ee6b}
clock stuff into a drawer.
\begin{verbatim}
(setq org-clock-into-drawer t)
(setq org-log-into-drawer t)
(setq org-clock-int-drawer "CLOCK")
\end{verbatim}
\subsection{LAST step: reload org}
\label{sec:org21cccce}

Ran into a \href{https://github.com/seagle0128/.emacs.d/issues/129}{strange error}, and reloading org at the end is the
solution:

\begin{verbatim}
(org-reload)
\end{verbatim}
\section{editing}
\label{sec:org580d36a}

The heart of editor is, well, editing. Many things are determining the
experience. Here are the ones I use to make editing quicker, easier,
less typing essentially.

\subsection{by packages}
\label{sec:org0439641}
\subsubsection{auto company}
\label{sec:orgda647f0}

A good auto completion thing. See details \href{https://company-mode.github.io/}{here}.

\begin{verbatim}
(use-package company
  :ensure t
  :config)
(add-hook 'prog-mode-hook 'global-company-mode)
\end{verbatim}
\subsubsection{undo tree}
\label{sec:orge65322a}

More \href{https://elpa.gnu.org/packages/undo-tree.html}{undos}?

\begin{verbatim}
(use-package undo-tree
  :ensure t
  :config
  (setq undo-tree-visualizer-timestamps t)
  (setq undo-tree-visualizer-diff t))
(global-undo-tree-mode)
\end{verbatim}
\subsubsection{search \& jump}
\label{sec:orgc21af8c}
\begin{enumerate}
\item ag
\label{sec:org314b1b1}
Use the silversearcher.
\begin{verbatim}
(use-package ag
  :ensure
  :config
  (setq ag-highlight-search t)
  (setq ag-reuse-buffers t))
\end{verbatim}

Follow the \href{https://github.com/emacsorphanage/helm-ag}{helm-ag manual}, "Insert thing at point as default search
pattern, if this value is non nil":

\begin{verbatim}
(setq helm-ag-insert-at-point 'symbol)
(setq helm-ag-use-temp-buffer t)
\end{verbatim}
\item dumb-jump
\label{sec:org5159961}

First, let's make sure we have \texttt{xref} because we will hook into the
xref backend:

\begin{verbatim}
(use-package xref
  :ensure
  :config)
\end{verbatim}

Now install \texttt{dumb-jump}:

\begin{verbatim}
(use-package dumb-jump
  :ensure
  :config
  (setq dumb-jump-prefer-searcher 'ag))
\end{verbatim}

Last, hook to \texttt{xref} to use \texttt{M.} bind:

\begin{verbatim}
(add-hook 'xref-backend-functions #'dumb-jump-xref-activate)
\end{verbatim}
\item ripgrep
\label{sec:org5fd2db7}
This enables searching recursively in projects.

\begin{verbatim}
(use-package ripgrep
  :ensure t)
(use-package projectile-ripgrep
  :ensure t
  :requires (ripgrep projectile))
\end{verbatim}

\item ace-jump-mode
\label{sec:orgaeae224}

Let's one jump around text

\begin{verbatim}
(use-package ace-jump-mode
  :ensure t
  :bind (("C-c C-SPC" . 'ace-jump-mode)
         ("C-c C-DEL" . 'ace-jump-mode-pop-mark)))
\end{verbatim}
\end{enumerate}

\subsubsection{max 80 cols wide}
\label{sec:org4e2cdec}
\begin{verbatim}
(use-package column-enforce-mode
  :ensure t
  :config
  (setq column-enforce-column 80)
  :bind ("C-c m" . 'column-enforce-mode))
;; column-enforce-face
\end{verbatim}
\subsubsection{highlight whitespace \& lines > 80 long}
\label{sec:org0bf5c0c}
Highlight unnecessary chars and lines over 80.
\begin{verbatim}
(use-package whitespace
  :ensure
  :config (setq whitespace-style '(face empty tabs lines-tail trailing))
  :config (global-whitespace-mode t))
\end{verbatim}

\subsubsection{browse kill ring}
\label{sec:orgb035017}

Don't use \texttt{popup-kill-ring} as it's dead. Use the \href{https://github.com/browse-kill-ring/browse-kill-ring}{browse-kill-ring}:

\begin{verbatim}
(use-package browse-kill-ring
  :ensure
  :config
  (setq browse-kill-ring-highlight-current-entry t)
  (setq browse-kill-ring-highlight-inserted-item t))

(browse-kill-ring-default-keybindings)
\end{verbatim}
\subsubsection{parenthesis}
\label{sec:org9b165b3}

Borrowing from old init.el:

\begin{verbatim}
(show-paren-mode t)
(set-face-attribute 'region nil
                    :background "#666"
                    :foreground "#d52349")
(set-face-background 'show-paren-match (face-background 'default))
(set-face-foreground 'show-paren-match "#d52349")
(set-face-attribute 'show-paren-match nil
                    :weight 'extra-bold)
\end{verbatim}

\begin{enumerate}
\item show matching delimiters (default: on)
\label{sec:orgad281b3}

Use \href{https://github.com/Fanael/rainbow-delimiters}{rainbow-delimiter}. Do not set the
\texttt{rainbow-delimiters-mismatched-face} because it will raise alarm all all
the following brackets when there is a mismatch, like a xmas lights,
and it's distracting to find out the actual mismatch!

\begin{verbatim}
(use-package rainbow-delimiters
  :ensure
  :config
  (set-face-attribute 'rainbow-delimiters-unmatched-face nil
                      :background "GhostWhite"))
(add-hook 'prog-mode-hook #'rainbow-delimiters-mode)
\end{verbatim}
\item type using smartparens (default: on)
\label{sec:orgc5a38e6}

Well, who wants to type parenthesis.

\begin{verbatim}
(use-package smartparens
  :ensure
  :config
  (require 'smartparens-config))
(add-hook 'prog-mode-hook #'smartparens-mode)
\end{verbatim}
\end{enumerate}
\subsubsection{string inflection (default: some modes)}
\label{sec:orgf498d90}

This is useful in coding to change a string to snake, camel and so on.

\begin{verbatim}
(use-package string-inflection
  :ensure
  :config)
(add-hook 'elpy-mode-hook
            '(lambda ()
               (local-set-key (kbd "C-q C-u")
                              'string-inflection-python-style-cycle)))
(add-hook 'org-mode-hook
            '(lambda ()
               (local-set-key (kbd "C-q C-u")
                              'string-inflection-python-style-cycle)))
(add-hook 'mu4e-compose-mode-hook
            '(lambda ()
               (local-set-key (kbd "C-q C-u")
                              'string-inflection-python-style-cycle)))
(add-hook 'js2-mode-hook
            '(lambda ()
               (local-set-key (kbd "C-q C-u")
                              'string-inflection-python-style-cycle)))
\end{verbatim}

\subsubsection{annotate-mode (default: some modes)}
\label{sec:orge622e3d}

The file-annotations are store externally. Seems to fail with
\texttt{args-out-of-range} and then Emacs is confused. (filed issue for this)

Also, it seems to interfere with colorful modes like \texttt{magit} or
\texttt{org-agenda-mode} so that I went with a whitelist instead of the wish of
a blacklist of modes.

Read more \href{https://github.com/bastibe/annotate.el}{here}.

\begin{verbatim}
(use-package annotate
  :ensure t

  ;; for ledger-mode, as 'C-c C-a' is taken there.
  :bind ("C-c C-A" . 'annotate-annotate)

  :config
  (add-hook 'org-mode 'annotate-mode)
  (add-hook 'csv-mode 'annotate-mode)
  (add-hook 'c-mode 'annotate-mode)
  (add-hook 'c++-mode 'annotate-mode)
  (add-hook 'sh-mode 'annotate-mode)
;;;  (define-globalized-minor-mode global-annotate-mode annotate-mode
;;;    (lambda () (annotate-mode 1)))
;;;  (global-annotate-mode 1)
  )
\end{verbatim}

\subsubsection{writeroom-mode (default: off)}
\label{sec:orgf847dd3}

It seems to be a particular way of changing the buffer look so the
writer can focus on, writing. Read \href{https://github.com/joostkremers/writeroom-mode}{more here}.

\begin{verbatim}
(use-package writeroom-mode
  :ensure t
  :config)
\end{verbatim}

\subsubsection{anzu}
\label{sec:org9e9ced4}

Show number of search matches.

\begin{verbatim}
(use-package
  anzu

  :ensure
  :config)
(global-anzu-mode +1)
\end{verbatim}

\subsubsection{move-text}
\label{sec:orgdd3b660}

Looks convenient \href{https://github.com/emacsfodder/move-text}{here}:
\begin{itemize}
\item \texttt{Meta-up} move-text-up (line or active region)
\item \texttt{Meta-down} move-text-down (line or active region)
\end{itemize}

\begin{verbatim}
  (use-package move-text
    :ensure
    :config)
(move-text-default-bindings)
\end{verbatim}

t** tabs to 2

These are global tab settings. Since TAB is such a sensitive thing,
each coding mode may have a different style/preference that will
override this.

\begin{verbatim}
(setq-default indent-tabs-mode nil)
(setq require-final-newline t)
(setq indent-line-function 'insert-tab)
(setq-default tab-width 2)
\end{verbatim}
\subsection{no trailing spaces}
\label{sec:orge180548}
\begin{verbatim}
(setq next-line-add-newlines nil)
(add-hook 'before-save-hook 'delete-trailing-whitespace)
\end{verbatim}
\subsection{iedit mode}
\label{sec:org8a48dc4}

Instead of using the string replacement, use this edit mode will
highlight all the occurances in the buffer, and now your editing will
take effect on all of them.

\begin{verbatim}
(global-set-key (kbd "C-M-i") 'iedit-mode)
\end{verbatim}

\section{buffers}
\label{sec:org1ded03f}

There are three concepts seem to me: desktop, window config, and buffers.

\begin{itemize}
\item desktop: is like virtual desktop, and you can have many, like i3.
\item window config: think of it like a look you have created using
buffers, eg. stack them this way or that way, on the same
desktop. So switching a window config will switch the buffer layout
within your current desktop.
\item buffer: is the building block.
\end{itemize}

\subsection{by packages}
\label{sec:orgca4ae00}
\subsubsection{multi desktops: eyebrowse}
\label{sec:org6894401}

Awesome window manager. It's like using i3m but inside emacs. Use the
\texttt{C-c C-w <0..9>} key to switch to so called desktop. On each desktop,
you can have different buffers open and so on, so I don't have to
close buffers, or \texttt{C-x b} a lot anymore. Look for details \href{https://depp.brause.cc/eyebrowse/}{here}.

\begin{verbatim}
  (use-package eyebrowse
    :ensure t)
(eyebrowse-mode t)
\end{verbatim}

\subsubsection{select buffer}
\label{sec:orgc69d81c}

\begin{verbatim}
(use-package ace-window
  :ensure
  :config
  (setq aw-ignore-current t)
  (setq aw-keys '(?a ?s ?d ?f ?g ?h ?j ?k ?l))
  (setq aw-background nil)
  (global-set-key (kbd "M-o") 'ace-window)
  (custom-set-faces
   '(aw-leading-char-face
     ((t (:inherit ace-jump-face-foreground
                   :background "GhostWhite"
                   :box nil)))))
)
\end{verbatim}

\subsubsection{buffer naming}
\label{sec:org480792e}
\begin{verbatim}
(use-package uniquify
  :init
  (setq uniquify-buffer-name-style 'post-forward-angle-brackets))
\end{verbatim}
\subsection{save \& restore buffers}
\label{sec:orgc3c44ea}

First, you need to create a folder \texttt{\textasciitilde{}/.emacs.d/savehist}. If not, upon
existing emacs, it will complain, asking you whether you want to
\texttt{ignore} it, answer \texttt{yes} will be fine. No harm. It's just the session
will not then be saved.

\begin{verbatim}

(setq desktop-path (list "~/.emacs.d/savehist"))
(setq desktop-dirname "~/.emacs.d/savehist")
(setq desktop-restore-eager 5)
(setq desktop-load-locked-desktop t)
(desktop-save-mode 1)

(savehist-mode 1)
(setq history-length t)
(setq history-delete-duplicates t)
(setq savehist-save-minibuffer-history 1)
(setq savehist-additional-variables '(kill-ring search-ring regexp-search-ring))

\end{verbatim}

But skip the followings:
\begin{verbatim}
(setq desktop-buffers-not-to-save
     (concat "\\("
             "^nn\\.a[0-9]+\\|\\.log\\|(ftp)\\|^tags\\|^TAGS"
             "\\|\\.emacs.*\\|\\.diary\\|\\.newsrc-dribble\\|\\.bbdb"
             "\\)$"))
(add-to-list 'desktop-modes-not-to-save 'dired-mode)
(add-to-list 'desktop-modes-not-to-save 'Info-mode)
(add-to-list 'desktop-modes-not-to-save 'info-lookup-mode)
(add-to-list 'desktop-modes-not-to-save 'fundamental-mode)
\end{verbatim}

\subsection{switch window config: winner-mode}
\label{sec:orgc728e99}

Read \href{https://www.emacswiki.org/emacs/WinnerMode}{here}. A config is essentially a look of buffers, and there can be
many, say, a config has two windows side by side, while another is 3
stacked. This mode will let you switch between them on the same desktop.

Enables \texttt{winner-mode}. Navigate buffer-window configs with \texttt{C-c left} and
\texttt{C-c right}.

\begin{verbatim}
(winner-mode 1)
\end{verbatim}

However, with eyebrowse, I think this is redundant function. Maybe I should skip this?

\subsection{toggle maximize buffer}
\label{sec:org9bd2440}

Temporarily maximize a buffer.  \href{https://gist.github.com/mads379/3402786}{found here}

\begin{verbatim}
(defun toggle-maximize-buffer () "Maximize buffer"
  (interactive)
  (if (= 1 (length (window-list)))
      (jump-to-register '_)
    (progn
      (window-configuration-to-register '_)
      (delete-other-windows))))
\end{verbatim}

Map it to a key.

\begin{verbatim}
(global-set-key [M-f8] 'toggle-maximize-buffer)
\end{verbatim}

\subsection{buffer decorations}
\label{sec:org97e4641}
Setup the visual cues about the current editing buffer
\begin{verbatim}
(column-number-mode t)
(setq visible-bell t)
(setq scroll-step 1)
(setq-default transient-mark-mode t)  ;; highlight selection
\end{verbatim}
\section{navigate file \& dir}
\label{sec:orgd164413}

I'm not quite used to using emacs as file manager yet. To me, it's
much easier to just start a shell and type.

Nonetheless, navigating code tree is necessary, and the one like CP is
so deeply buried that having a good navigator is probably a good
thing.

The most dramatic thing is \hyperref[sec:org090dfeb]{treemacs}, which I need some time to get
used to. It looks nice, but feels a bit, exaggerated to my taste.

\subsection{dir hack}
\label{sec:orgc4825c9}
\begin{verbatim}
(use-package dash
  :ensure
  :config)

(use-package dired-hacks-utils
  :ensure
  :config)
\end{verbatim}
\subsection{dired-rainbow}
\label{sec:orge13eb4a}

Make the dired coloful. Copied from \href{https://github.com/Fuco1/dired-hacks}{dired-hacks}.

\begin{verbatim}
(use-package dired-rainbow
  :ensure
  :config
  (progn
    (dired-rainbow-define-chmod directory "#6cb2eb" "d.*")
    (dired-rainbow-define html "#eb5286" ("css" "less" "sass" "scss" "htm" "html" "jhtm" "mht" "eml" "mustache" "xhtml"))
    (dired-rainbow-define xml "#f2d024" ("xml" "xsd" "xsl" "xslt" "wsdl" "bib" "json" "msg" "pgn" "rss" "yaml" "yml" "rdata"))
    (dired-rainbow-define document "#9561e2" ("docm" "doc" "docx" "odb" "odt" "pdb" "pdf" "ps" "rtf" "djvu" "epub" "odp" "ppt" "pptx"))
    (dired-rainbow-define markdown "#ffed4a" ("org" "etx" "info" "markdown" "md" "mkd" "nfo" "pod" "rst" "tex" "textfile" "txt"))
    (dired-rainbow-define database "#6574cd" ("xlsx" "xls" "csv" "accdb" "db" "mdb" "sqlite" "nc"))
    (dired-rainbow-define media "#de751f" ("mp3" "mp4" "MP3" "MP4" "avi" "mpeg" "mpg" "flv" "ogg" "mov" "mid" "midi" "wav" "aiff" "flac"))
    (dired-rainbow-define image "#f66d9b" ("tiff" "tif" "cdr" "gif" "ico" "jpeg" "jpg" "png" "psd" "eps" "svg"))
    (dired-rainbow-define log "#c17d11" ("log"))
    (dired-rainbow-define shell "#f6993f" ("awk" "bash" "bat" "sed" "sh" "zsh" "vim"))
    (dired-rainbow-define interpreted "#38c172" ("py" "ipynb" "rb" "pl" "t" "msql" "mysql" "pgsql" "sql" "r" "clj" "cljs" "scala" "js"))
    (dired-rainbow-define compiled "#4dc0b5" ("asm" "cl" "lisp" "el" "c" "h" "c++" "h++" "hpp" "hxx" "m" "cc" "cs" "cp" "cpp" "go" "f" "for" "ftn" "f90" "f95" "f03" "f08" "s" "rs" "hi" "hs" "pyc" ".java"))
    (dired-rainbow-define executable "#8cc4ff" ("exe" "msi"))
    (dired-rainbow-define compressed "#51d88a" ("7z" "zip" "bz2" "tgz" "txz" "gz" "xz" "z" "Z" "jar" "war" "ear" "rar" "sar" "xpi" "apk" "xz" "tar"))
    (dired-rainbow-define packaged "#faad63" ("deb" "rpm" "apk" "jad" "jar" "cab" "pak" "pk3" "vdf" "vpk" "bsp"))
    (dired-rainbow-define encrypted "#ffed4a" ("gpg" "pgp" "asc" "bfe" "enc" "signature" "sig" "p12" "pem"))
    (dired-rainbow-define fonts "#6cb2eb" ("afm" "fon" "fnt" "pfb" "pfm" "ttf" "otf"))
    (dired-rainbow-define partition "#e3342f" ("dmg" "iso" "bin" "nrg" "qcow" "toast" "vcd" "vmdk" "bak"))
    (dired-rainbow-define vc "#0074d9" ("git" "gitignore" "gitattributes" "gitmodules"))
    (dired-rainbow-define-chmod executable-unix "#38c172" "-.*x.*")
    ))

\end{verbatim}
\subsection{dired-narrow}
\label{sec:org64f681a}
\begin{verbatim}
(use-package dired-narrow
  :ensure
  :config)
\end{verbatim}
\subsection{dired-collapse}
\label{sec:org367d67e}
\begin{verbatim}
(use-package dired-collapse
  :ensure
  :config)
\end{verbatim}
\subsection{dired-filter}
\label{sec:orgc9902b4}
\begin{verbatim}
(use-package dired-filter
  :ensure
  :config)
\end{verbatim}
\subsection{treemacs (default: off)}
\label{sec:org090dfeb}
Copied from \href{https://github.com/Alexander-Miller/treemacs\#installation}{here}. I'm leaving this mode off by default. \texttt{C-c t t} to
enable it.

\begin{verbatim}
(use-package treemacs
  :ensure t
  :defer t
  :init
  (with-eval-after-load 'winum
    (define-key winum-keymap (kbd "M-0") #'treemacs-select-window))
  :config
  (progn
    (setq treemacs-collapse-dirs                 (if treemacs-python-executable 3 0)
          treemacs-deferred-git-apply-delay      0.5
          treemacs-directory-name-transformer    #'identity
          treemacs-display-in-side-window        t
          treemacs-eldoc-display                 t
          treemacs-file-event-delay              5000
          treemacs-file-extension-regex          treemacs-last-period-regex-value
          treemacs-file-follow-delay             0.2
          treemacs-file-name-transformer         #'identity
          treemacs-follow-after-init             t
          treemacs-git-command-pipe              ""
          treemacs-goto-tag-strategy             'refetch-index
          treemacs-indentation                   2
          treemacs-indentation-string            " "
          treemacs-is-never-other-window         nil
          treemacs-max-git-entries               5000
          treemacs-missing-project-action        'ask
          treemacs-move-forward-on-expand        nil
          treemacs-no-png-images                 nil
          treemacs-no-delete-other-windows       t
          treemacs-project-follow-cleanup        nil
          treemacs-persist-file                  (expand-file-name ".cache/treemacs-persist" user-emacs-directory)
          treemacs-position                      'left
          treemacs-recenter-distance             0.1
          treemacs-recenter-after-file-follow    nil
          treemacs-recenter-after-tag-follow     nil
          treemacs-recenter-after-project-jump   'always
          treemacs-recenter-after-project-expand 'on-distance
          treemacs-show-cursor                   nil
          treemacs-show-hidden-files             t
          treemacs-silent-filewatch              nil
          treemacs-silent-refresh                nil
          treemacs-sorting                       'alphabetic-asc
          treemacs-space-between-root-nodes      t
          treemacs-tag-follow-cleanup            t
          treemacs-tag-follow-delay              1.5
          treemacs-user-mode-line-format         nil
          treemacs-user-header-line-format       nil
          treemacs-width                         35
          treemacs-workspace-switch-cleanup      nil)

    ;; The default width and height of the icons is 22 pixels. If you are
    ;; using a Hi-DPI display, uncomment this to double the icon size.
    ;;(treemacs-resize-icons 44)

    (treemacs-follow-mode t)
    (treemacs-filewatch-mode t)
    (treemacs-fringe-indicator-mode t)
    (pcase (cons (not (null (executable-find "git")))
                 (not (null treemacs-python-executable)))
      (`(t . t)
       (treemacs-git-mode 'deferred))
      (`(t . _)
       (treemacs-git-mode 'simple))))
  :bind
  (:map global-map
        ("M-0"       . treemacs-select-window)
        ("C-x t 1"   . treemacs-delete-other-windows)
          ("C-x t t"   . treemacs)
          ("C-x t B"   . treemacs-bookmark)
          ("C-x t C-t" . treemacs-find-file)
          ("C-x t M-t" . treemacs-find-tag)))


  (use-package treemacs-icons-dired
    :after treemacs dired
    :ensure t
      :config (treemacs-icons-dired-mode))

  (use-package treemacs-projectile
    :after treemacs projectile
    :ensure t)
  (use-package treemacs-magit
    :after treemacs magit
    :ensure t)
\end{verbatim}

Add some files to ignore, eg. \textasciitilde{}.pyc`:

\begin{verbatim}
(with-eval-after-load 'treemacs
  (defun treemacs-ignore-gitignore (file _)
    (string= file ".pyc"))
  (push #'treemacs-ignore-gitignore treemacs-ignored-file-predicates))
\end{verbatim}

\section{Helm}
\label{sec:org9c0fca6}

Helm should really has its own section because it touches everything!

I just took over the config described in this \href{https://tuhdo.github.io/helm-intro.html}{helm intro}.

\begin{verbatim}
(use-package helm
 :ensure t
 :delight helm-mode
 :config
  (require 'helm-config)
  ;; The default "C-x c" is quite close to "C-x C-c", which quits Emacs.
  ;; Changed to "C-c h". Note: We must set "C-c h" globally, because we
  ;; cannot change `helm-command-prefix-key' once `helm-config' is loaded.
  (global-set-key (kbd "C-c h") 'helm-command-prefix)
  (global-unset-key (kbd "C-x c"))

  (define-key helm-map (kbd "<tab>") 'helm-execute-persistent-action) ; rebind tab to run persistent action
  (define-key helm-map (kbd "C-M-x") 'helm-execute-persistent-action) ; make TAB work in terminal
  (define-key helm-map (kbd "C-z")  'helm-select-action) ; list actions using C-z

  (when (executable-find "curl")
    (setq helm-google-suggest-use-curl-p t))

  (setq helm-split-window-inside-p            t ; open helm buffer inside current window, not occupy whole other window
        helm-move-to-line-cycle-in-source     t ; move to end or beginning of source when reaching top or bottom of source.
        helm-ff-search-library-in-sexp        t ; search for library in `require' and `declare-function' sexp.
        helm-scroll-amount                    8 ; scroll 8 lines other window using M-<next>/M-<prior>
        helm-ff-file-name-history-use-recentf t
        helm-echo-input-in-header-line t)

  (setq helm-autoresize-max-height 50)
  (setq helm-autoresize-min-height 0)
  (helm-autoresize-mode 1)

  (setq helm-M-x-fuzzy-match t)
  (setq helm-buffers-fuzzy-matching t
        helm-recentf-fuzzy-match    t)
  (setq helm-semantic-fuzzy-match t
        helm-imenu-fuzzy-match    t)
(setq helm-locate-fuzzy-match t)
(setq helm-apropos-fuzzy-match t)
(setq helm-lisp-fuzzy-completion t)
(helm-mode 1)

  (global-set-key (kbd "M-x") 'helm-M-x))
\end{verbatim}

Found \href{https://www.reddit.com/r/emacs/comments/30yer0/helm\_and\_recentf\_tips/}{this reddit post} of using \texttt{helm-mini}:

\begin{verbatim}
(setq helm-mini-default-sources '(helm-source-buffers-list
                                  helm-source-recentf
                                  helm-source-bookmarks
                                  helm-source-buffer-not-found))
\end{verbatim}

\section{Write chinese}
\label{sec:org140d6d4}
I have been using this one w/ reasonable success.
\begin{verbatim}
(use-package pyim
  :ensure
  :defer 10
  :config
  ;; 激活 basedict 拼音词库
  (use-package pyim-basedict
    :ensure nil
    :config (pyim-basedict-enable))

  ;; 五笔用户使用 wbdict 词库
  ;; (use-package pyim-wbdict
  ;;   :ensure nil
  ;;   :config (pyim-wbdict-gbk-enable))

  (setq default-input-method "pyim")

  ;; 我使用全拼
  (setq pyim-default-scheme 'quanpin)

  ;; 设置 pyim 探针设置，这是 pyim 高级功能设置，可以实现 *无痛* 中英文切换 :-)
  ;; 我自己使用的中英文动态切换规则是：
  ;; 1. 光标只有在注释里面时，才可以输入中文。
  ;; 2. 光标前是汉字字符时，才能输入中文。
  ;; 3. 使用 M-j 快捷键，强制将光标前的拼音字符串转换为中文。
  (setq-default pyim-english-input-switch-functions
                '(pyim-probe-dynamic-english
                  pyim-probe-isearch-mode
                  pyim-probe-program-mode
                  pyim-probe-org-structure-template))

  (setq-default pyim-punctuation-half-width-functions
                '(pyim-probe-punctuation-line-beginning
                  pyim-probe-punctuation-after-punctuation))

  ;; 开启拼音搜索功能
  ;; (pyim-isearch-mode 1)

  ;; 使用 pupup-el 来绘制选词框
  (setq pyim-page-tooltip 'popup)

  ;; 选词框显示5个候选词
  (setq pyim-page-length 5)

  ;; 让 Emacs 启动时自动加载 pyim 词库
  (add-hook 'emacs-startup-hook
            #'(lambda () (pyim-restart-1 t)))
  :bind
  (;与 pyim-probe-dynamic-english 配合
  ("M-j" . pyim-convert-code-at-point)

   ("C-;" . pyim-delete-word-from-personal-buffer)))
   (setq default-input-method "pyim")
   (global-set-key (kbd "C-\\") 'toggle-input-method)
\end{verbatim}
\section{Office stuff}
\label{sec:org1fdd010}
Using emacs in a corporate env can be daunting.

\subsection{mu4e email}
\label{sec:org83ca39d}
mu4e only a emac client. The workhorse are davmail, isync and mu. You need to install these offline and hook them up using the config below.

\subsubsection{install \& minimal setup}
\label{sec:org2b9243e}
First thing first, load the package. As you can see, I have used \texttt{apt-get} install mu4e.

\begin{verbatim}
(add-to-list 'load-path "/usr/share/emacs/site-lisp/mu4e/")
(require 'mu4e)
\end{verbatim}

Then we load \texttt{maildirs-extension}:

\begin{verbatim}
(use-package mu4e-maildirs-extension
  :ensure
  :config)
(mu4e-maildirs-extension)
\end{verbatim}

Now, we tell emacs I want to use \texttt{mu4e} as email client:

\begin{verbatim}
(setq mail-user-agent 'mu4e-user-agent)
\end{verbatim}

Link to a couple modes to help me writing good emails:
\begin{verbatim}
(add-hook 'mu4e-compose-mode-hook
              (lambda ()
                (visual-line-mode t)
                (writegood-mode t)
                (flyspell-mode t)))
\end{verbatim}
\subsubsection{how to get mails}
\label{sec:orga1660e3}
Setup location of my maildir.
\begin{verbatim}
(setq mu4e-maildir (expand-file-name "~/Maildir"))
\end{verbatim}

Sync email by calling \texttt{mbsync}:
\begin{verbatim}
(setq mu4e-get-mail-command "mbsync -a")
\end{verbatim}

How often should I check? Value in seconds:
\begin{verbatim}
(setq mu4e-update-interval 600)
\end{verbatim}

Setup some common folders:
\begin{verbatim}
(setq mu4e-drafts-folder "/drafts"
      mu4e-sent-folder   "/sent"
      mu4e-trash-folder  "/trash")
\end{verbatim}

Setup some shortcuts as bookmarks:
\begin{verbatim}
(add-to-list
 'mu4e-bookmarks
 '("flag:attach"
   "Messages with attachment"
   ?a) t)

(add-to-list
 'mu4e-bookmarks
 '("size:5M..500M"
   "Big messages"
   ?b) t)

(add-to-list
 'mu4e-bookmarks
 '("flag:flagged"
   "Flagged messages"
   ?f) t)
\end{verbatim}

\subsubsection{list view}
\label{sec:orgce27f1a}
Customize the list view header:
\begin{verbatim}
(setq mu4e-headers-date-format "%b-%d %a"
      mu4e-headers-fields '((:date . 10)
                            (:flags . 5)
                            (:recipnum . 3)
                            (:from-or-to . 10)
                            (:thread-subject . nil)))
\end{verbatim}

Skip duplicates:

\begin{verbatim}
(setq mu4e-headers-skip-duplicates t)
\end{verbatim}

Showing related in a tree fashion so I know the context:

\begin{verbatim}
(setq mu4e-headers-include-related t)
\end{verbatim}

Here is a fun one. I noticed that the email thread grows like that greedy snake game, a pretty good sign that the team is malfunctioning :) So we add a displayed number on the number of recipients, and just watch it grow:
\begin{verbatim}
(add-to-list 'mu4e-header-info-custom
             '(:recipnum .
                         ( :name "Number of recipients"  ;; long name, as seen in the message-view
                                 :shortname "R#"           ;; short name, as seen in the headers view
                                 :help "Number of recipients for this message" ;; tooltip
                                 :function (lambda (msg)
                                             (format "%d"
                                                     (+ (length (mu4e-message-field msg :to))
                                                        (length (mu4e-message-field msg :cc))))))))

\end{verbatim}
\subsubsection{read \& attachment}
\label{sec:org016c820}
Save attachment to:

\begin{verbatim}
(setq mu4e-attachment-dir "~/Downloads")
\end{verbatim}

To open HTML in browser:
\begin{verbatim}
(add-to-list 'mu4e-view-actions
             '("ViewInBrowser" . mu4e-action-view-in-browser)
             t)
\end{verbatim}

Attempt to show images when viewing messages:

\begin{verbatim}
(setq mu4e-view-show-images t)
\end{verbatim}

Use imagemagick, if available:

\begin{verbatim}
(when (fboundp 'imagemagick-register-types)
  (imagemagick-register-types))
\end{verbatim}
\subsubsection{write new}
\label{sec:orgda97385}
My signature line:

\begin{verbatim}
(setq mu4e-compose-signature
      (concat
       "Best regards,\n\n"
       "Feng Xia\n"
       "W: http://www.mycompany.com\n"))
\end{verbatim}
\subsubsection{send}
\label{sec:org4ebc34a}
Sending email is to use SMTP. Here I'm showing to use the company one
through \texttt{davmail} which runs smtp listen on port \texttt{1025}. You can also
use Gmail/hotmail:

\begin{verbatim}
(use-package smtpmail
  :ensure t
  :config
  (setq send-mail-function 'smtpmail-send-it
        user-mail-address "fxia1@mycompany.com"
        smtpmail-debug-info t
        smtpmail-smtp-user "fxia1@mycompany.com"
        smtpmail-default-smtp-server "localhost"
        smtpmail-auth-credentials (expand-file-name "~/.authinfo")
        smtpmail-smtp-service 1025
        smtpmail-stream-type nil
        starttls-use-gnutls nil
        starttls-extra-arguments nil))
\end{verbatim}

There is a toggle where you can queue the sending email first instead
of sending to server immediately. This is useful for travel when you
just write, then queue, then when reconnected to the internect, send.

\begin{verbatim}
(setq smtpmail-queue-mail nil
      smtpmail-queue-dir "~/Maildir/queue/cur")
\end{verbatim}
\subsubsection{reply}
\label{sec:org8f501d6}
When replying an email, auto fill in my info:
\begin{verbatim}
(setq mu4e-compose-reply-to-address "fxia1@mycompany.com"
      user-mail-address "fxia1@mycompany.com"
      user-full-name "Feng Xia"
      message-signature  (concat
                          "Feng Xia\n"
                          "http://snapshots.world.s3-website.ap-northeast-2.amazonaws.com/\n")
      message-citation-line-format "On %Y-%m-%d %H:%M:%S, %f wrote:"
      message-citation-line-function 'message-insert-formatted-citation-line
      mu4e-headers-results-limit 500)
\end{verbatim}
\subsubsection{kill all buffer upon exit}
\label{sec:org4a8d6d7}
mu4e can open a lot of writing buffers. Just kill them all when we exit mu4e:

\begin{verbatim}
(setq message-kill-buffer-on-exit t)
\end{verbatim}
\subsubsection{write html}
\label{sec:orga9705b7}
Emacs doesn't like html email body. Nor do I. But one thing I found
out is that markdown mode table will look terrible as plain text on
receiving end. There are a couple ways to work around.

\begin{enumerate}
\item write in org
\label{sec:org51232d6}
So we now write email in org mode, then call \texttt{M-x org-mime-htmlize} to
convert either the whole buffer or a region to html before sending:

\begin{verbatim}
(use-package org-mime
  :ensure
  :config
  (setq org-mime-export-ascii 'utf-8))
\end{verbatim}

\item write in markdown
\label{sec:org126c982}

How about writing it in markdown? You don't need to do much. Switch to
\texttt{markdown-mode} to write, then switch back to \texttt{mu4e-compose-mode} and
then \texttt{C-c C-c} to send:

\begin{verbatim}
(defun multipart-html-message (plain html)
  "Creates a multipart HTML email with a text part and an html part."
  (concat "<#multipart type=alternative>\n"
          "<#part type=text/plain>"
          plain
          "<#part type=text/html>\n"
          html
          "<#/multipart>\n"))

(defun convert-message-to-markdown ()
  "Convert the message in the current buffer to a multipart HTML email.

The HTML is rendered by treating the message content as Markdown."
  (interactive)
  (unless (executable-find "pandoc")
    (error "Pandoc not found, unable to convert message"))
  (let* ((begin
          (save-excursion
            (goto-char (point-min))
            (search-forward mail-header-separator)))
         (end (point-max))
         (html-buf (generate-new-buffer "*mail-md-output*"))
         (exit-code
          (call-process-region begin end "pandoc" nil html-buf nil
                               "--quiet" "-f" "gfm" "-t" "html"))
         (html (format "<html>\n<head></head>\n<body>\n%s\n</body></html>\n"
                (with-current-buffer html-buf
                  (buffer-substring (point-min) (point-max)))))
         (raw-body (buffer-substring begin end)))
    (when (not (= exit-code 0))
      (error "Markdown conversion failed, see %s" (buffer-name html-buf)))
    (with-current-buffer html-buf
      (set-buffer-modified-p nil)
      (kill-buffer))
    (undo-boundary)
    (delete-region begin end)
    (save-excursion
      (goto-char begin)
      (newline)
      (insert (multipart-html-message raw-body html)))))

(defun message-md-send (&optional arg)
  "Convert the current buffer and send it.
If given prefix arg ARG, skips markdown conversion."
  (interactive "P")
  (unless arg
    (convert-message-to-markdown))
  (message-send))

(defun message-md-send-and-exit (&optional arg)
  "Convert the current buffer and send it, then exit from mail buffer.
If given prefix arg ARG, skips markdown conversion."
  (interactive "P")
  (unless arg
    (convert-message-to-markdown))
  (message-send-and-exit))

(with-eval-after-load 'message
 (define-key message-mode-map (kbd "C-c C-s") #'message-md-send)
 (define-key message-mode-map (kbd "C-c C-c") #'message-md-send-and-exit))
\end{verbatim}
\end{enumerate}
\section{Hobbies}
\label{sec:org2a75643}
\subsection{elfeed}
\label{sec:org5085744}

Read news:
\begin{verbatim}
(use-package elfeed
  :ensure
  :config)
(setq elfeed-feeds
      '(("http://rss.slashdot.org/Slashdot/slashdotMain" dev)
        ("https://fengxia41103.github.io/myblog/feeds/all.atom.xml" me)
        ("https://www.reddit.com/r/aww+jokes.rss" fun)))
(use-package elfeed-goodies
  :ensure
  :config)
(elfeed-goodies/setup)
\end{verbatim}

\subsection{taskjuggler}
\label{sec:org26753eb}
\begin{verbatim}
(use-package tj3-mode
  :ensure t
  :after org-plus-contrib
  :config
  (require 'ox-taskjuggler)
  (custom-set-variables
   '(org-taskjuggler-process-command "/usr/local/bin/tj3 --silent --no-color --output-dir %o %f")
   '(org-taskjuggler-project-tag "PRJ")))
\end{verbatim}

\section{Coding}
\label{sec:orgd91c51a}

Big part of my life is taken by coding. So here it is, all the coding
related stuff.
\subsection{taskjuggler-mode (tj3-mode)}
\label{sec:org865f05d}
\begin{verbatim}
(use-package tj3-mode
  :ensure t
  :after org-plus-contrib
  :config
  (require 'ox-taskjuggler)
  (custom-set-variables
   '(org-taskjuggler-process-command "/usr/local/bin/tj3 --silent --no-color --output-dir %o %f")
   '(org-taskjuggler-project-tag "PRJ")))
\end{verbatim}
\subsection{Version control}
\label{sec:org358e8a5}
\subsubsection{magit}
\label{sec:org53d4598}

Add the powerful Magit

\begin{verbatim}
(use-package magit
  :ensure t
  :defer
  :config
  (add-hook 'after-save-hook 'magit-after-save-refresh-status t)
  :bind ("C-x g" . 'magit-status))
(use-package magit-todos
  :ensure t
  :defer)
(use-package
  magit-gitflow

  :ensure
  :config (add-hook 'magit-mode-hook 'turn-on-magit-gitflow))
\end{verbatim}
\subsubsection{monky}
\label{sec:org2f8f91b}
Add the Magit-copy for Mercurial 'monky'

\begin{verbatim}
(use-package monky
  :ensure t
  :defer
  :bind ("C-x m" . 'monky-status))
\end{verbatim}
\subsubsection{git informations in gutter}
\label{sec:org97e3e7b}
\begin{verbatim}
(use-package git-gutter-fringe+
  :ensure t
  :defer
  :if window-system
  :bind ("C-c g" . 'git-gutter+-mode))
\end{verbatim}
\subsubsection{speedup VCS}
\label{sec:org48c9129}
Regexp matching directory names that are not under VC's control. The
default regexp prevents fruitless and time-consuming attempts to
determine the VC status in directories in which filenames are
interpreted as hostnames.

\begin{verbatim}
(defvar locate-dominating-stop-dir-regexp
  "\\`\\(?:[\\/][\\/][^\\/]+\\|/\\(?:net\\|afs\\|\\.\\.\\.\\)/\\)\\'")
\end{verbatim}
\subsubsection{global caller}
\label{sec:orgb34da25}

Have a single binding to call the most appropriate tool given the repository.

\begin{verbatim}
(defun paf/vcs-status ()
     (interactive)
     (condition-case nil
         (magit-status-setup-buffer)
       (error (monky-status))))

(global-set-key (kbd "C-M-x v") 'paf/vcs-status)
\end{verbatim}

\subsection{Projectile}
\label{sec:orgf0adbad}

Start using projectile. It has the documentation \href{https://docs.projectile.mx/en/latest/}{here}.

\begin{verbatim}
(use-package projectile
  :ensure t
  :config
  (define-key projectile-mode-map (kbd "C-c p") 'projectile-command-map)
  (setq projectile-completion-system 'helm)
  (projectile-mode +1))

(use-package helm-projectile
  :ensure t
  :after projectile
  :requires projectile
  :delight projectile-mode
  :config
  (helm-projectile-on))
\end{verbatim}

Search the entire project with \texttt{C-c p s s} for a regexp. This let's
you turn the matching results into an editable buffer using \texttt{C-c
C-e}. Other keys are listed \href{https://github.com/syohex/emacs-helm-ag\#keymap}{here}.

\begin{verbatim}
(use-package helm-ag
  :ensure t
  :config)
\end{verbatim}

I havae used it by a \texttt{M-?} binding. It's just old habit:
\begin{verbatim}
(global-set-key (kbd "M-?") 'helm-ag)
\end{verbatim}

\subsection{debug w/ GDB}
\label{sec:orge831571}
\subsubsection{{\bfseries\sffamily TODO} Make it so that the source frame placement is forced only when using gdb.}
\label{sec:orgcfc2186}

\begin{verbatim}
(setq gdb-many-windows t)
(setq gdb-use-separate-io-buffer t)

(defun easy-gdb-top-of-stack-and-restore-windows ()
  (interactive)
  (switch-to-buffer (gdb-stack-buffer-name))
  (goto-char (point-min))
  (gdb-select-frame)
  (gdb-restore-windows)
  (other-window 2))

(global-set-key (kbd "C-x C-a C-t") 'easy-gdb-top-of-stack-and-restore-windows)
\end{verbatim}

This should display the source code always in the same window when debugging.
Found on \href{https://stackoverflow.com/questions/39762833/emacsgdb-customization-how-to-display-source-buffer-in-one-window}{Stack Overflow}.
\begin{verbatim}
; This unfortunately also messes up the regular frame navigation of source code.
;(add-to-list 'display-buffer-alist
;             (cons 'cdb-source-code-buffer-p
;                   (cons 'display-source-code-buffer nil)))

(defun cdb-source-code-buffer-p (bufName action)
  "Return whether BUFNAME is a source code buffer."
  (let ((buf (get-buffer bufName)))
    (and buf
         (with-current-buffer buf
           (derived-mode-p buf 'c++-mode 'c-mode 'csharp-mode 'nxml-mode)))))

(defun display-source-code-buffer (sourceBuf alist)
  "Find a window with source code and set sourceBuf inside it."
  (let* ((curbuf (current-buffer))
         (wincurbuf (get-buffer-window curbuf))
         (win (if (and wincurbuf
                       (derived-mode-p sourceBuf 'c++-mode 'c-mode 'nxml-mode)
                       (derived-mode-p (current-buffer) 'c++-mode 'c-mode 'nxml-mode))
                  wincurbuf
                (get-window-with-predicate
                 (lambda (window)
                   (let ((bufName (buffer-name (window-buffer window))))
                     (or (cdb-source-code-buffer-p bufName nil)
                         (assoc bufName display-buffer-alist)
                         ))))))) ;; derived-mode-p doesn't work inside this, don't know why...
    (set-window-buffer win sourceBuf)
    win))
\end{verbatim}

Here is my cheatsheet for the keyboard commands:

All prefixed with \texttt{C-x C-a}

\begin{center}
\begin{tabular}{llc}
\hline
Domain & Command & C-<key>\\
\hline
Breakpoint & set & b\\
 & temporary & t\\
 & delete & d\\
\hline
Execute & Next & n\\
 & Step Into & s\\
 & Return / Finish & f\\
 & Continue (run) & r\\
\hline
Stack & Up & <\\
 & Down & >\\
\hline
Execute & Until current line & u\\
(rarer) & Single instruction & i\\
 & Jump to current line & j\\
\hline
\end{tabular}
\end{center}
\subsection{editing}
\label{sec:orgf6367fe}
\subsubsection{diffing}
\label{sec:org4209ed5}
\href{https://github.com/justbur/emacs-vdiff}{
vdiff} let's one compare buffers or files.

\begin{verbatim}
(use-package vdiff
  :ensure t
  :config
  ; This binds commands under the prefix when vdiff is active.
  (define-key vdiff-mode-map (kbd "C-c") vdiff-mode-prefix-map))
\end{verbatim}

\subsubsection{yasnippet}
\label{sec:org74deb3e}
Let's first see how far I get with file-based capture templates and yankpad.

\begin{verbatim}
  (use-package yasnippet
    :ensure t)
  (use-package auto-yasnippet
    :ensure t
:after yasnippet
    :config
    (bind-key "C-M-x C-s c" 'aya-create)
    (bind-key "C-M-x C-s e" 'aya-expand))
\end{verbatim}

\subsubsection{commenting out}
\label{sec:org0d89a59}
Easy commenting out of lines.

\begin{verbatim}
(autoload 'comment-out-region "comment" nil t)
(global-set-key (kbd "C-c q") 'comment-out-region)
\end{verbatim}

\subsubsection{deduplicate and sort}
\label{sec:org2ee7fbd}
Help cleanup the includes and using lists.
\href{http://www.emacswiki.org/emacs/DuplicateLines}{found here}

\begin{verbatim}
(defun uniquify-region-lines (beg end)
  "Remove duplicate adjacent lines in region."
  (interactive "*r")
  (save-excursion
    (goto-char beg)
    (while (re-search-forward "^\\(.*\n\\)\\1+" end t)
      (replace-match "\\1"))))

(defun paf/sort-and-uniquify-region ()
  "Remove duplicates and sort lines in region."
  (interactive)
  (sort-lines nil (region-beginning) (region-end))
  (uniquify-region-lines (region-beginning) (region-end)))
\end{verbatim}

Simplify cleanup of \texttt{\#include} / \texttt{typedef} / \texttt{using} blocks.

\begin{verbatim}
(global-set-key (kbd "C-M-x s") 'paf/sort-and-uniquify-region)
\end{verbatim}
\subsubsection{selective display (default: off)}
\label{sec:org29c0edb}
Will fold all text indented more than the position of the cursor at
the time the keys are pressed.

\begin{verbatim}
(defun set-selective-display-dlw (&optional level)
  "Fold text indented more than the cursor.
   If level is set, set the indent level to level.
   0 displays the entire buffer."
  (interactive "P")
  (set-selective-display (or level (current-column))))

(global-set-key "\C-x$" 'set-selective-display-dlw)
\end{verbatim}
\subsection{IRC}
\label{sec:org72a3a13}
Use \texttt{circe}.
\begin{verbatim}
(use-package
  circe
    :ensure
    :config(
            setq circe-network-options '((
                                          "Freenode" :tls t
                                          :nick "fengxia41103"
                                          :channels ("#emacs"
                                                     "#python"
                                                     "#odoo"
                                                     "#reactjs"
                                                     "#latex")))))
(use-package
  helm-circe

  :ensure
  :config)
\end{verbatim}

\subsection{languages}
\label{sec:org78f58dc}

These are minor modes to handle programming language specifics which
are often termed as development rules agreed by the team.
\subsubsection{markdown}
\label{sec:org6ac447b}
Enough to handle my Markdown needs.

\begin{verbatim}
(use-package writegood-mode
  :ensure
  :config)

(use-package
  markdown-mode

  :ensure
  :config
  (add-to-list 'auto-mode-alist '("\\.md\\'" . markdown-mode)
  (add-hook 'markdown-mode-hook
            (lambda ()
              (visual-line-mode t)
              (writegood-mode t)
              (flyspell-mode t)))))
\end{verbatim}
\subsubsection{C/C++}
\label{sec:org15bdee6}
\begin{enumerate}
\item header/implementation toggle
\label{sec:orgbdda376}

Switch from header to implementation file quickly.
\begin{verbatim}
(add-hook 'c-mode-common-hook
          (lambda ()
            (local-set-key  (kbd "C-c o") 'ff-find-other-file)))
\end{verbatim}
\item no indentation of namespaces in C++
\label{sec:orga75c898}
Essentially, use the Google C++ style formatting.
\begin{verbatim}
(use-package google-c-style
  :ensure t
  :config
  (add-hook 'c-mode-common-hook 'google-set-c-style)
  (add-hook 'c-mode-common-hook 'google-make-newline-indent))

(use-package flymake-google-cpplint
  :ensure t)
\end{verbatim}
\end{enumerate}
\subsubsection{python}
\label{sec:orgccafedc}

Setup an IDE:

\begin{verbatim}
(use-package elpy
  :ensure
  :init
  (elpy-enable))
\end{verbatim}

ELPY has its own indentation mode, which is overriding the one I use
globally, so disable this one:

\begin{verbatim}
(add-hook 'elpy-mode-hook (lambda () (highlight-indentation-mode -1)))
\end{verbatim}

\begin{enumerate}
\item py-autopep8
\label{sec:org9ed82f8}
Add hook to reformat python code based on pep8 spec. You need to
install \texttt{pip install autopep8} offline.

\begin{verbatim}
(use-package
  py-autopep8

  :ensure t
  :config
  (add-hook 'python-mode-hook 'py-autopep8-enable-on-save)
  (setq py-autopep8-options '("--max-line-length=80")))
\end{verbatim}
\item py-isort
\label{sec:org0b4be65}
Sort python import. Need to install \texttt{pip install isort} offline.

\begin{verbatim}
(use-package
  py-isort

  :ensure
  :config
  (add-hook 'before-save-hook 'py-isort-before-save)
  (setq py-isort-options '("-sl")))
\end{verbatim}
\item smartparens
\label{sec:orge4bf277}
\begin{verbatim}
(add-hook 'python-mode-hook #'smartparens-mode)
\end{verbatim}
\end{enumerate}
\subsubsection{web-mode}
\label{sec:org263febc}
web-mode with config for Polymer editing
\begin{verbatim}
(use-package web-mode
  :ensure t
  :config
  (setq web-mode-enable-current-element-highlight t)
  (setq web-mode-enable-current-column-highlight t)
  (setq web-mode-enable-css-colorization t))
\end{verbatim}

Who should use this mode:
\begin{verbatim}
(add-to-list 'auto-mode-alist '("\\.html\\'" . web-mode))
(add-to-list 'auto-mode-alist '("\\.tpl\\.php\\'" . web-mode))
(add-to-list 'auto-mode-alist '("\\.[agj]sp\\'" . web-mode))
(add-to-list 'auto-mode-alist '("\\.as[cp]x\\'" . web-mode))
(add-to-list 'auto-mode-alist '("\\.erb\\'" . web-mode))
(add-to-list 'auto-mode-alist '("\\.mustache\\'" . web-mode))
(add-to-list 'auto-mode-alist '("\\.ftl\\'" . web-mode))
\end{verbatim}
\subsubsection{web-beautify}
\label{sec:orgb7eb209}
This is actually depending on \texttt{js-beautify}. See \href{https://github.com/yasuyk/web-beautify}{web-beautify} for
details.

\begin{verbatim}
(use-package web-beautify
  :ensure
  :config)
(add-hook 'js2-mode-hook
          (lambda ()
            (add-hook 'before-save-hook 'web-beautify-js-buffer t t)))
(add-hook 'json-mode-hook
          (lambda ()
            (add-hook 'before-save-hook 'web-beautify-js-buffer t t)))
(add-hook 'web-mode-hook
          (lambda ()
            (add-hook 'before-save-hook 'web-beautify-html-buffer t t)))
(add-hook 'css-mode-hook
          (lambda ()
            (add-hook 'before-save-hook 'web-beautify-css-buffer t t)))
(add-hook 'html-mode-hook
          (lambda ()
            (add-hook 'before-save-hook 'web-beautify-html-buffer t t)))
\end{verbatim}
\subsubsection{\href{https://github.com/smihica/emmet-mode}{emmet-mode}}
\label{sec:orgeee6ede}
Useful abbreviations when coding in HTML. See \href{https://github.com/rooney/zencoding}{zencoding} for details.

\begin{verbatim}
(use-package emmet-mode
  :ensure t
  :after(web-mode css-mode scss-mode)
  :config)
(setq emmet-expand-jsx-className? t)
(setq emmet-move-cursor-between-quotes t)
(add-hook 'emmet-mode-hook (lambda () (setq emmet-indent-after-insert nil)))
(add-hook 'sgml-mode-hook 'emmet-mode)
(add-hook 'web-mode-hook 'emmet-mode)
(add-hook 'css-mode-hook  'emmet-mode)
(add-hook 'scss-mode-hook  'emmet-mode)
\end{verbatim}
\subsubsection{javascript family: .js .ts .jsx}
\label{sec:orgddd980e}
There are a couple packages for .js files.

\begin{enumerate}
\item js2-mode
\label{sec:org6507fca}
First, use \texttt{js2-mode} to handle \texttt{.js} and \texttt{.jsx} files.

\begin{verbatim}
(use-package js2-mode
    :ensure
    :config)

(add-to-list 'auto-mode-alist '("\\.js[x]\\'" . js2-mode))
(add-to-list 'auto-mode-alist '("\\.ts\\'" . js2-mode))
(add-hook 'js2-mode-hook #'smartparens-mode)

\end{verbatim}

\item prettier-js
\label{sec:orgc4e1412}
Link js2-mode to prettier to beautify my code.
\begin{verbatim}
(use-package prettier-js
  :ensure
  :config
  (setq prettier-js-args '(
                           "--trailing-comma" "es5"
                           "--single-quote" "false"
                           "--print-width" "80"
                           "--tab-width" "2"
                           )));
(add-hook 'js2-mode-hook 'prettier-js-mode)
(add-hook 'json-mode-hook 'prettier-js-mode)
(add-hook 'js-mode-hook 'prettier-js-mode)
\end{verbatim}

\item js-doc
\label{sec:org87ad9e0}
Nothing is complete without a doc solution.

\begin{verbatim}
(use-package js-doc
  :ensure
  :config
  (setq js-doc-mail-address "fxia1@mycompany.com")
  (setq js-doc-author (format "Feng Xia <%s>" js-doc-mail-address))
  (setq js-doc-url "http://www.mycompany.com")
  (setq js-doc-license "Company License")
)
(add-hook 'js2-mode-hook
          #'(lambda ()
              (define-key js2-mode-map "\C-ci" 'js-doc-insert-function-doc)
              (define-key js2-mode-map "@" 'js-doc-insert-tag)))

\end{verbatim}
\end{enumerate}
\subsubsection{csv}
\label{sec:org4859fc1}
mode to edit CSV files.
\begin{verbatim}
(use-package csv-mode
  :ensure t
  :mode "\\.csv\\'")
\end{verbatim}
\subsubsection{json}
\label{sec:org026a42d}

This should be installed before the javascript stuff because I'll be
using the \texttt{prettier} as beautifier.

\begin{verbatim}
(use-package json-mode
  :ensure
  :config)
\end{verbatim}
\subsubsection{yaml}
\label{sec:org9c4dd88}

Details are \href{https://github.com/yoshiki/yaml-mode}{here}.

\begin{verbatim}
(use-package yaml-mode
  :ensure
  :config)
(add-to-list 'auto-mode-alist '("\\.yml\\'" . yaml-mode))
(add-hook 'yaml-mode-hook
          '(lambda ()
        (define-key yaml-mode-map "\C-m" 'newline-and-indent)))
\end{verbatim}
\subsection{LAST: enforce my tab style}
\label{sec:orgf0adae6}

Found this \href{https://github.com/syl20bnr/spacemacs/issues/5923}{here}, and I like it, to set my styles in a central
location. This was researched while battling the .js tab level. I
don't want to use the \texttt{customize} way since that will be a hidden
manual step after a fresh install.

First, define a func to include my indent settings. It takes an input
argument:

\begin{verbatim}
(defun my-setup-indent (n)
  ;; java/c/c++
  (setq-local standard-indent n)
  (setq-local c-basic-offset n)

  ;; javascript family
  (setq-local javascript-indent-level n) ; javascript-mode
  (setq-local js-indent-level n) ; js-mode
  (setq-local js2-basic-offset n) ; js2-mode
  (setq-local js-switch-indent-offset n) ; js-mode
  (setq-local javascript-indent-level n) ; javacript-mode
  (setq-local react-indent-level n) ; react-mode
  (setq-local js2-basic-offset n)

  ;; html, css
  (setq-local web-mode-attr-indent-offset n) ; web-mode
  (setq-local web-mode-code-indent-offset n) ; web-mode, js code in html file
  (setq-local web-mode-css-indent-offset n) ; web-mode, css in html file
  (setq-local web-mode-markup-indent-offset n) ; web-mode, html tag in html file
  (setq-local web-mode-sql-indent-offset n) ; web-mode
  (setq-local web-mode-attr-value-indent-offset n) ; web-mode
  (setq web-mode-comment-style 2) ;; web-mode
  (setq-local css-indent-offset n) ; css-mode

  ;; shells
  (setq-local sh-basic-offset n) ; shell scripts
  (setq-local sh-indentation n))
\end{verbatim}

Now set the tabs:

\begin{verbatim}
(defun my-personal-code-style ()
  (interactive)
  (message "My personal code style!")
  ;; use space instead of tab
  (setq indent-tabs-mode nil)
  ;; indent 2 spaces width
  (my-setup-indent 2))

;; it would be lovely if this was enough, but it gets stomped on by modes.
(my-personal-code-style)
\end{verbatim}

So, to enfore this on some modes:
\begin{verbatim}
(add-hook 'css-mode-hook 'my-personal-code-style)
(add-hook 'js2-mode-hook 'my-personal-code-style)
(add-hook 'react-mode-hook 'my-personal-code-style)
(add-hook 'sh-mode-hook 'my-personal-code-style)
\end{verbatim}
\end{document}
